### 2017-01-22 previous-paper-analysis/previous-paper-analysis.tex
Starting previous paper analysis

\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\title{Previous Paper Analysis}
\date{January 24, 2017}
\author{Shawn Seymour}

\begin{document}

\maketitle

\newpage

\begin{thebibliography}{9}

\bibitem{grove}
	Molly Grove,
	\emph{Heuristics for the Generalized Traveling Salesman Problem},
	UMM CSci Senior Seminar Conference, Fall 2015, Morris, MN.

\end{thebibliography}

\end{document}

### 2017-01-22 previous-paper-analysis/previous-paper-analysis.tex
Draft of previous paper analysis

@@
 \usepackage[margin=1in]{geometry}
+\usepackage[doublespacing]{setspace}
 
@@
 
-\newpage
+I read Molly Grove's paper, \emph{Heuristics for the Generalized Traveling Salesman Problem}, from the Fall 2015 senior seminar conference \cite{grove}.
+Her paper details three heuristics, also known as approximation algorithms, for the generalized traveling salesman problem (GTSP).
+The paper introduces the topic and gives background information on graph theory, computational complexity, and the mathematical definition of the original traveling salesman problem (TSP) and the GTSP.
+
+The structure of the paper is very clear.
+Each section has a clear point; The paper starts with an introduction, gives background information we'll need to know to analyze the heuristics, and then details 3 different heuristics for the GTSP.
+Each heuristic is broken into clear parts (as the given heuristics are combinations of different algorithms) and each part of the heuristic is described as a subsection.
+
+For the most part, one paper per heuristic is used to analyze the heuristic and its algorithms.
+A few sources are used to provide background information on the problem, on computational complexity, and on certain algorithms relied upon in the presented heuristics.
+
+The sources used by Grove are almost all recent papers at the time the paper was written.
+The key sources for the heuristics were all within 5 years and most of her supporting sources were within 7 years.
+The only source that stood out as being old was her reference [4] written by Papadimitriou and Steiglitz, which was published in 1982.
+
+Grove presents the material with diagrams and explanations of the algorithms that each heuristic uses.
+As the TSP and GTSP are graph problems, she uses helpful diagrams of nodes and edges and shows how the heuristics work on the given graph.
+These are very helpful to understand the different clustering techniques that are used in a couple of the given heuristics.
+
+The paper was fairly easy to understand although some of the specifics got complicated.
+There were some subsections that were quite mathematically heavy and a few of these examples or formulas could have been explained a bit simpler for a data-structures level student.
+I believe the structure for presenting the material was quite good but a few of the specifics could have been explained in simpler terms.
+
+I really liked the paper's structure and presentation of the different heuristics.
+Each heuristic is broken up based on the mathematics behind it and the algorithms and techniques used which is how I would do it.
+For some of the explanations, I would have simplified some things or provided clearer examples of certain techniques presented in the paper.
+\newline
 

### 2017-02-21 annotated-bibliography/annotated-bibliography.tex
Adding past annotated bibliography

\documentclass [11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue
}

\urlstyle{same}

\title{Vertex Coloring\\\medskip Annotated Bibliography}
\author{Shawn Seymour\\University of Minnesota Morris}
\date{Febuary 7, 2017}

\begin{document}
\maketitle
\section*{Summary}
The vertex coloring problem (VCP) is one of the most researched problems in graph theory. A proper vertex coloring is an assignment of colors, or labels, to each vertex in a graph \(G = (V, E)\) such that no edge connects to vertices of the same color. The VCP aims to find the chromatic number, denoted \(\chi(G)\), the minimum number of colors needed to properly color a graph as defined above. There are many heuristics to solve this NP-hard problem as well as ways to estimate and put bounds on the chromatic number, which I will explore in this paper.

\nocite{*}
\bibliographystyle{IEEEannot}
\bibliography{../references.bib}
\end{document}

### 2017-02-21 paper/paper.tex
Starting paper

% This is a sample document using the University of Minnesota, Morris, Computer Science
% Senior Seminar modification of the ACM sig-alternate style. Much of this content is taken
% directly from the ACM sample document illustrating the use of the sig-alternate class. Certain
% parts that we never use have been removed to simplify the example, and a few additional
% components have been added.

% See https://github.com/UMM-CSci/Senior_seminar_templates for more info and to make
% suggestions and corrections.

\documentclass{sig-alternate}
\usepackage{color}
\usepackage[colorinlistoftodos]{todonotes}

%%%%% Uncomment the following line and comment out the previous one
%%%%% to remove all comments
%%%%% NOTE: comments still occupy a line even if invisible;
%%%%% Don't write them as a separate paragraph
%\newcommand{\mycomment}[1]{}

\begin{document}

% --- Author Metadata here ---
%%% REMEMBER TO CHANGE THE SEMESTER AND YEAR AS NEEDED
\conferenceinfo{UMM CSci Senior Seminar Conference, December 2015}{Morris, MN}

\title{Vertex Coloring}

\numberofauthors{1}

\author{
\alignauthor
Shawn S. Seymour\\
	\affaddr{Division of Science and Mathematics}\\
	\affaddr{University of Minnesota, Morris}\\
	\affaddr{Morris, Minnesota, USA 56267}\\
	\email{seymo079@morris.umn.edu}
}

\maketitle
\begin{abstract}
Abstract goes here...
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\bibliographystyle{abbrv}
\bibliography{../references}

\end{document}

### 2017-02-21 paper/update.sh

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+latexmk -pdf paper.tex
+

### 2017-02-21 paper/paper.tex
Adding key point stuff

@@
 %%% REMEMBER TO CHANGE THE SEMESTER AND YEAR AS NEEDED
-\conferenceinfo{UMM CSci Senior Seminar Conference, December 2015}{Morris, MN}
+\conferenceinfo{UMM CSci Senior Seminar Conference, May 2017}{Morris, MN}
 
-\title{Vertex Coloring}
+\title{Conflict-Free Vertex Coloring Of Planar Graphs}
 
@@
 
+\section*{KEY POINTS}
+The goal of this research is to discover and explain properties and results of conflict-free coloring of planar graphs.
+The conflict-free coloring problem is a variation of the classical vertex coloring problem (VCP).
+The VCP aims to color a graph \(G = (V, E)\) such that no two adjacent vertices receive the same color.
+This is typically shown in the form of the \emph{k-colorability} problem: a graph is \emph{k-colorable} if it can be colored using $k$ or less colors.
+For example, the map of the 48 contiguous states can be colored with 4 colors and is thus \emph{4-colorable}.
+This is shown in the famous four-color theorem.
+It cannot be colored with 3 colors, and is thus \emph{not 3-colorable}.
+
+The minimum amount of colors needed to color a graph is called the \emph{chromatic number}.
+It is heavily studied in graph theory and it is NP-hard to determine the chromatic number of a graph.
+This property makes it an interesting problem to study as there are currently no known polynomial time algorithms to solve the VCP.
+
+A conflict-free coloring is a variation of the VCP.
+Each vertex must be assigned a color such that for every vertex $v$, there is at least one color appearing exactly once in the neighborhood of $v$, i.e.
+vertices adjacenct to $v$.
+
 \section{Introduction}
 \label{sec:introduction}
+Explain why graph coloring, specifically vertex coloring, is interesting and how it can be used to solve many real-world applications.
+Describe how it can be one of the most difficult problems to solve efficiently.
+Bring up the example of coloring the 48 contiguous states, an example of a planar graph.
+Introduce conflict-free coloring as a variant of the classical vertex coloring problem (VCP).
+
+\section{Background}
+\label{sec:background}
+Give some of the needed background regarding graph theory, complexity theory (i.e. NP-complete, NP-hard, etc), and the classical vertex coloring problem.
+
+\subsection{Graphs}
+\label{sec:graphs}
+Define what a graph, \(G = (V, E)\), is. Define terms that will be used throughout the paper dealing with graphs such as nodes, edges, neighborhoods, etc.
+
+\subsection{Vertex Coloring Problem (VCP)}
+\label{sec:vcp}
+Explain the classical vertex coloring problem and why it is interesting. Give required background so conflict-free colorings will make sense later.
+
+\subsection{Complexity of the VCP}
+\label{sec:complexitytheory}
+
+\section{Conclusions}
+
+\section{Acknowledgments}
+Give thanks to my mom, etc.
+
+\cite{bondy1976graph}
 

### 2017-02-21 paper/paper.tex
Key points and outline

@@
 \section*{KEY POINTS}
-The goal of this research is to discover and explain properties and results of conflict-free coloring of planar graphs.
+The goal of this research is to discover and explain properties and results of conflict-free (C-F) coloring of planar graphs.
 The conflict-free coloring problem is a variation of the classical vertex coloring problem (VCP).
@@
 Each vertex must be assigned a color such that for every vertex $v$, there is at least one color appearing exactly once in the neighborhood of $v$, i.e.
-vertices adjacenct to $v$.
+vertices adjacent to $v$.
+My primary source by Abel et al.
+\cite{abel2017three} focuses on results of conflict-free colorings of general graphs and then moves into the specific case of planar graphs.
+
+There are many complexity results relating to conflict-free colorings.
+Conflict-free coloring is reduced from the \emph{k-colorability} to show that it is NP-hard.
+We know that \emph{k-colorability} is NP-hard through a reduction from 3-SAT.
+The reduction of \emph{3-SAT} to \emph{k-colorability} is given in \cite{sharma2012new}.
+This source then goes on to give results for C-F coloring of planar graphs.
+For example, \cite{abel2017three} give results on the NP-completeness of deciding whether planar graphs can be C-F colored with 1 or 2 colors.
+Conflict-free coloring of planar graphs can always be done with 3 colors, but minimizing the colors used is NP-hard, like the original VCP.
+
+For general graphs, there are complexity results given by \cite{gargano2015complexity}.
+They show that conflict-free coloring of closed neighborhoods (when a node does not belong to its neighborhood) is NP-complete.
+They give non-approximability results for the conflict-free coloring of open neighborhoods.
 
@@
 \label{sec:background}
-Give some of the needed background regarding graph theory, complexity theory (i.e. NP-complete, NP-hard, etc), and the classical vertex coloring problem.
+Give some of the needed background regarding graph theory, complexity theory (i.e.
+NP-complete, NP-hard, etc), and the classical vertex coloring problem.
+Background information will generally come from \cite{bondy1976graph}.
 
@@
 \label{sec:graphs}
-Define what a graph, \(G = (V, E)\), is. Define terms that will be used throughout the paper dealing with graphs such as nodes, edges, neighborhoods, etc.
+Define what a graph, \(G = (V, E)\), is. Define terms that will be used throughout the paper dealing with graphs such as nodes, edges, neighborhoods, what a planar graph is, etc.
 
@@
 
-\subsection{Complexity of the VCP}
+\subsection{Complexity Theory}
 \label{sec:complexitytheory}
+Define common complexity theory terms such as P, NP, NP-complete, and NP-hard. Talk about the complexity of the classical VCP and define other knowledge needed to talk about complexity.
+
+\section{C-F Coloring of General Graphs}
+Discuss conflict-free coloring of general graphs, i.e. graphs that can be non-planar.
+\section{C-F Coloring of Planar Graphs}
+Discuss conflict-free coloring of planar graphs.
+
+\section{Complexity of Coloring C-F Graphs}
+Discuss the complexity of coloring C-F graphs.
+
+\subsection{General Graphs}
+\subsubsection{Open Neighborhoods}
+This is when the neighborhood of a node does not include the node itself.
+
+\subsubsection{Closed Neighborhoods}
+This is when the neighborhood of the node includes the node itself. Talk about result that conflict-free coloring of closed neighborhoods is NP-complete from \cite{gargano2015complexity}.
+
+\subsection{Planar Graphs}
+Look at the complexity results given in \cite{abel2017three} at coloring planar graphs.
 
 \section{Conclusions}
+Brief summary of the findings and results explained above.
 
 \section{Acknowledgments}
-Give thanks to my mom, etc.
-
-\cite{bondy1976graph}
+Give thanks to my mom, Peter, Elena, etc.
 

### 2017-02-27 paper/paper.tex
Starting introduction and background

--- 2017-02-21 paper/paper.tex
@@
-% This is a sample document using the University of Minnesota, Morris, Computer Science
-% Senior Seminar modification of the ACM sig-alternate style. Much of this content is taken
-% directly from the ACM sample document illustrating the use of the sig-alternate class. Certain
-% parts that we never use have been removed to simplify the example, and a few additional
-% components have been added.
-
-% See https://github.com/UMM-CSci/Senior_seminar_templates for more info and to make
-% suggestions and corrections.
-
 \documentclass{sig-alternate}
@@
 
-% --- Author Metadata here ---
-%%% REMEMBER TO CHANGE THE SEMESTER AND YEAR AS NEEDED
-\conferenceinfo{UMM CSci Senior Seminar Conference, December 2015}{Morris, MN}
+\conferenceinfo{UMM CSci Senior Seminar Conference, May 2017}{Morris, MN}
 
-\title{Vertex Coloring}
+\title{Conflict-Free Vertex Coloring Of Planar Graphs}
 
@@
 
+Consider the map of the 48 contiguous states in the United States of America.
+Suppose we would like to color each state such that no two states that share a boundary have the same color.
+This problem can be modeled with a mathematical structure called a \emph{graph}.
+We can represent each state with a \emph{vertex} and represent a boundary between two states with an \emph{edge}.
+This map is an example of a planar graph, i.e.
+none of the edges cross when drawn on a plane.
+
+This is a famous example of the \emph{vertex coloring} problem and one of many graph coloring problems.
+The vertex coloring problem aims to find the minimum amount of colors needed to color a graph such that no two adjacent vertices are colored with the same color.
+While some problems are relatively easy to solve, the vertex coloring problem is one of the most computationally complex problems in computer science and mathematics.
+The vertex coloring problem has many real-world applications such as exam timetabling, register allocation, and the scheduling of taxis.
+
+The \emph{conflict-free coloring} problem is a relaxed variation of the vertex coloring problem.
+The conflict-free coloring problem does not aim to color every vertex such that it is not connected to a vertex of the same color.
+Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one colored vertex.
+
+\section{Background}
+\label{sec:background}
+To understand the problem, the algorithms to solve it, and its results, we must first understand some graph theory, some computational complexity theory, and the precise definitions of the vertex coloring problem and the conflict-free coloring problem.
+
+\subsection{Graph Theory}
+\label{sec:graphtheory}
+
+A graph, denoted $G=(V,E)$, is an ordered pair of two sets: a set of vertices $V$ and a set of edges $E$.
+Each edge consists of a pair of vertices from $V$.
+For example, $(u,w) \in E$ is an edge connecting vertices $u$ and $w$ where $u,w \in V$.
+Vertices are adjacent if they are connected by an edge.
+A graph can be non-technically described as a set of points (vertices) with lines (edges) connecting them.
+A simple graph is an undirected graph where each edge connects two different vertices and no two edges connect the same pair of vertices.
+This means a vertex cannot have a loop, i.e.
+an edge from a vertex to itself.
+\cite{bondy1976graph}
+
+The neighborhood of a vertex, denoted $N_G(v)$, is a set of all vertices adjacent to $v$.
+A \emph{closed} neighborhood consists of all vertices adjacent to $v$ and $v$ itself.
+Unless stated otherwise, we will assume when talking about neighborhoods that they are closed neighborhoods.
+The degree of a vertex, denoted $d_G(v)$, is the number of vertices adjacent to $v$.
+The maximum degree of a graph $G$, denoted $\Delta(G)$, is the maximum degree of its vertices.
+
+\subsection{Graph Coloring}
+\label{sec:coloring}
+A vertex coloring is an assignment of colors to each vertex of a graph $G$ such that no adjacent vertices share the same color.
+Mathematically, it can be described as a function $f : V \rightarrow S = \{1, 2, \dots, k\}$ such that $\forall u,w \in V$, if $(u,w) \in E$, then $f(u) \neq f(w)$.
+The \emph{chromatic number} of $G$, denoted $\chi(G)$, is the minimum number of colors, i.e.
+$|S|$, needed to properly color $G$.
+
+\subsection{Complexity Theory}
+\label{sec:complexitytheory}
+
+\section{C-F Coloring of General Graphs}
+
+\section{C-F Coloring of Planar Graphs}
+
+\section{Complexity of Coloring C-F Graphs}
+
+\subsection{General Graphs}
+
+\subsection{Planar Graphs}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+\section{Acknowledgments}
+\cite{abel2017three}
+
 \bibliographystyle{abbrv}

### 2017-02-27 paper/paper.tex
Adding more background, section draft almost done

@@
 an edge from a vertex to itself.
-\cite{bondy1976graph}
 
@@
 The maximum degree of a graph $G$, denoted $\Delta(G)$, is the maximum degree of its vertices.
+\cite{bondy1976graph}
 
@@
 $|S|$, needed to properly color $G$.
+The \emph{vertex coloring} problem, when given a simple graph $G$, is to find $\chi(G)$.
+\cite{bondy1976graph}
 
-\subsection{Complexity Theory}
+A graph $G$ is said to be \emph{k-colorable} if it can be colored using $k$ or fewer colors, i.e.
+$\chi(G) \leq k$.
+A graph having $\chi(G) = k$ is said to be a \emph{k-chromatic} graph.
+The \emph{k-colorability} problem asks if a graph can be colored using $k$ colors.
+This problem is a slightly easier problem than the vertex coloring problem as it is decision problem rather than an optimization problem.
+
+A \emph{conflict-free coloring} of a graph assigns one of $k$ colors to some of the vertices such that, for every vertex $v$, there is a color that is assigned to exactly one vertex among $v$ and $v$'s neighbors.
+A \emph{conflict-free k-coloring} of a simple graph $G$ assigns one of $k$ different colors to a subset $S \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the closed neighborhood of $v$.
+The vertex $u$ can be thought of the \emph{conflict-free neighbor} of $v$.
+The \emph{conflict-free chromatic number} of G, denoted $\chi_{CF}(G)$, is the smallest $k$ for which a conflict-free coloring exists.
+\cite{abel2017three}
+
+\subsection{Computational Complexity Theory}
 \label{sec:complexitytheory}
+A \emph{decision} problem, as mentioned earlier, is a problem that can be answered with a `yes' or a `no' \cite{sipser2006introduction}.
+A decision problem is said to be in the class \emph{P} if in the worst case, it can be solved with an algorithm that runs in polynomial time.
+A problem can be solved in polynomial time if an algorithm with input size $n$ can run in at most $n^k$ steps where $k$ is a constant that does not depend on $n$.
+
+Given a decision problem and information showing what the answer is, it can be possible to verify the answer quickly.
+If a decision problem can be verified in polynomial time but not solved in polynomial time, it is said to be in the class \emph{NP}.
+Take note that this does not exclude problems in class \emph{P}; \emph{P} is a subset of \emph{NP}.
+The \emph{k-colorability} problem is an example of a problem in NP.
+There are currently no known polynomial-time algorithms to solve the VCP but it can be verified in polynomial time.
+\cite{garey2002computers}
+
+There are certain problems that can be proven to be as hard as every problem in NP.
+There problems are said to be NP-hard.
+A problem is NP-hard if it every problem in NP can be polynomially reduced to it.
+This brings an important result: if an NP-hard problem can be solved with an algorithm that runs in polynomial time, then any problem in NP could be solved in polynomial time.
+A decision problem is said to be \emph{NP-complete} when it is both in NP and NP-hard.
+
+The vertex coloring problem (VCP) and the conflict-free coloring problem (CFCP) are not in the class NP as they are not decision problems.
+A common approach to proving problems as NP-hard or NP-complete is reducing them from a known NP problem.
+If we find a known hard problem $Y$, then we can prove that another problem $X$ is hard by reducing $Y$ to $X$.
+The VCP and the CFCP have both been shown to be NP-hard \cite{abel2017three,moret1998theory}.
+The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, a well-known NP-complete problem \cite{sharma2012new}.
 

### 2017-02-28 paper/paper.tex
Adding section draft stuff

@@
 \begin{abstract}
-Abstract goes here...
+The conflict-free coloring problem is a variation of the vertex coloring problem, a classical NP-hard optimization problem.
+The conflict-free coloring problem aims to color the vertices of a graph in a way where every vertex is connected to at least one uniquely colored vertex.
 \end{abstract}
@@
 The conflict-free coloring problem does not aim to color every vertex such that it is not connected to a vertex of the same color.
-Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one colored vertex.
+Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one uniquely colored vertex.
 

### 2017-03-20 paper/paper.tex
Adding some initial figures and making revisions to background

@@
 
-\conferenceinfo{UMM CSci Senior Seminar Conference, May 2017}{Morris, MN}
+\conferenceinfo{UMM CSci Senior Seminar Conference, April 2017}{Morris, MN}
 
@@
 Suppose we would like to color each state such that no two states that share a boundary have the same color.
-This problem can be modeled with a mathematical structure called a \emph{graph}.
+This problem can be modeled with a graph.
 We can represent each state with a \emph{vertex} and represent a boundary between two states with an \emph{edge}.
@@
 This is a famous example of the \emph{vertex coloring} problem and one of many graph coloring problems.
-The vertex coloring problem aims to find the minimum amount of colors needed to color a graph such that no two adjacent vertices are colored with the same color.
+The vertex coloring problem aims to find the minimum number of colors needed to color a graph such that no two adjacent vertices are colored with the same color.
 While some problems are relatively easy to solve, the vertex coloring problem is one of the most computationally complex problems in computer science and mathematics.
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=7cm]{../figures/example.pdf}
+	\caption{A simple, undirected graph $H$}\label{fig:graph}
+\end{figure}
+
 \subsection{Graph Theory}
@@
 Vertices are adjacent if they are connected by an edge.
-A graph can be non-technically described as a set of points (vertices) with lines (edges) connecting them.
 A simple graph is an undirected graph where each edge connects two different vertices and no two edges connect the same pair of vertices.
-This means a vertex cannot have a loop, i.e.
-an edge from a vertex to itself.
+All graphs used by the vertex coloring problem and conflict-free coloring problem will be undirected, simple graphs.
+An example graph that we will use later on is shown in figure \ref{fig:graph}.
 
@@
 \cite{bondy1976graph}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=7cm]{../figures/example-vcp.pdf}
+	\caption{A minimum vertex coloring of $H$}\label{fig:vcp-example}
+\end{figure}
+
+\todo[inline]{The figures will be shaded with angled lines eventually}
 
@@
 This problem is a slightly easier problem than the vertex coloring problem as it is decision problem rather than an optimization problem.
+An example of a 3-colorable graph and a vertex coloring is shown in figure \ref{fig:vcp-example}.
 
-A \emph{conflict-free coloring} of a graph assigns one of $k$ colors to some of the vertices such that, for every vertex $v$, there is a color that is assigned to exactly one vertex among $v$ and $v$'s neighbors.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=7cm]{../figures/example-cfcp.pdf}
+	\caption{A minimum conflict-free coloring of $H$}\label{fig:cfcp-example}
+\end{figure}
+
+A \emph{conflict-free coloring} of a graph assigns one of $k$ colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
 A \emph{conflict-free k-coloring} of a simple graph $G$ assigns one of $k$ different colors to a subset $S \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the closed neighborhood of $v$.
@@
 \cite{abel2017three}
+
+An example of a conflict-free coloring is shown in figure \ref{fig:cfcp-example}.
+It is worth noting that all proper vertex colorings are also conflict-free colorings.
+This is because in a proper vertex coloring, every vertex is its own conflict-free neighbor \cite{abel2017three}.
 
@@
 Given a decision problem and information showing what the answer is, it can be possible to verify the answer quickly.
-If a decision problem can be verified in polynomial time but not solved in polynomial time, it is said to be in the class \emph{NP}.
+If a decision problem can be verified in polynomial time but not necessarily solved in polynomial time, it is said to be in the class \emph{NP}.
 Take note that this does not exclude problems in class \emph{P}; \emph{P} is a subset of \emph{NP}.
-The \emph{k-colorability} problem is an example of a problem in NP.
-There are currently no known polynomial-time algorithms to solve the VCP but it can be verified in polynomial time.
-\cite{garey2002computers}
 
@@
 The vertex coloring problem (VCP) and the conflict-free coloring problem (CFCP) are not in the class NP as they are not decision problems.
-A common approach to proving problems as NP-hard or NP-complete is reducing them from a known NP problem.
+A common approach to proving problems as NP-hard or NP-complete is a reduction from a known NP problem.
 If we find a known hard problem $Y$, then we can prove that another problem $X$ is hard by reducing $Y$ to $X$.
@@
 
-\section{C-F Coloring of General Graphs}
+\section{CF Coloring of General Graphs}
 
-\section{C-F Coloring of Planar Graphs}
+\section{CF Coloring of Planar Graphs}
 
-\section{Complexity of Coloring C-F Graphs}
-
-\subsection{General Graphs}
-
-\subsection{Planar Graphs}
+\section{Complexity of Coloring CF Graphs}
 

### 2017-03-20 paper/paper.tex
Adding algorithm and chugging along

@@
 \usepackage[colorinlistoftodos]{todonotes}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 
@@
 The conflict-free coloring problem aims to color the vertices of a graph in a way where every vertex is connected to at least one uniquely colored vertex.
+This paper presents heuristics to solve the conflict-free coloring problem on both general graphs and planar graphs.
+This paper also looks into bounds on the number of colors needed.
 \end{abstract}
@@
 Mathematically, it can be described as a function $f : V \rightarrow S = \{1, 2, \dots, k\}$ such that $\forall u,w \in V$, if $(u,w) \in E$, then $f(u) \neq f(w)$.
+A vertex coloring that satisfies this constraint is called a \emph{proper coloring}.
 The \emph{chromatic number} of $G$, denoted $\chi(G)$, is the minimum number of colors, i.e.
@@
 This is because in a proper vertex coloring, every vertex is its own conflict-free neighbor \cite{abel2017three}.
+We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(H) = 3$ and $\chi_{CF}(H) = 2$.
+
+The domination number of $G$, denoted $\gamma(G)$, is the size of a minimum dominating set of G.
+A dominating set is a subset $D$ of $V$ such that every vertex not in $D$ is adjacent to at least one vertex in $D$.
+The \emph{conflict-free domination number} for some $k$, denoted $\gamma_{CF}^k(G)$, is the minimum number of vertices that have to be colored in a conflict-free k-coloring of $G$.
+An example of a dominating set is $\{3, 5\}$ of graph $H$ where $\gamma(H) = 2$.
 
@@
 \section{CF Coloring of General Graphs}
+For the rest of this paper, we will consider the NP-complete problem of conflict-free k-colorability.
+Given a graph $G$ and an integer $k$, determine if graph $G$ can be colored using $k$ or fewer colors.
+Although all graphs can be conflict-free colored, a given graph $G$ may not be able to be colored with $k$ colors.
+
+As shown with graph $H$ in section \ref{sec:background}, even though all proper vertex colorings are also conflict-free colorings, fewer colors can usually be used.
+This leads us to use heuristics that differ from the vertex coloring problem.
+Abel et al.
+\cite{abel2017three} present an efficient heuristic to color certain general graphs with $k$ colors in a conflict-free manner.
+They call this heuristic \emph{iterated elimination of distance-3-sets}.
+
+\subsection{Guaranteeing CF k-Colorability}
+It is wasteful to spend time coloring a graph that cannot be conflict-free colored with $k$ colors.
+This leads Abel et al.
+\cite{abel2017three} to provide sufficient criterion to guarantee the conflict-free k-colorability of a graph.
+To introduce this criterion, we need to define a few more terms.
+
+\subsection{Iterated Elimination of Distance-3-Sets}
+
+\begin{algorithm}
+\caption{Iterated elimination of distance-3-sets} \label{alg:elimination}
+\begin{algorithmic}[1]
+\State $i \gets 1$, $\chi \gets \emptyset$
+\State Remove all isolated paths from $G$
+\While{$G$ is not empty}
+	\State $D \gets \emptyset$
+	\ForAll{components of $G$}
+		\State Pick a vertex $v$ and add it to $D$
+		\While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+			\State Pick $u$ at distance 3 from some vertex in $D$
+			\State $D \gets D \cup \{ w \}$
+		\EndWhile
+		\ForAll{$u \in D$}
+			\State Color $u$ with color $i$
+		\EndFor
+		\State $i \gets i + 1$
+		\State Remove $N[D]$ from $G$
+		\State Remove all isolated paths from G
+	\EndFor
+\EndWhile
+\State Color all removed isolated paths using color $i$
+\end{algorithmic}
+\end{algorithm}
 

### 2017-03-21 paper/paper.tex
Adding more work on CF coloring

@@
 \usepackage[noend]{algpseudocode}
+
+\newtheorem{theorem}{Theorem}
 
@@
 	\includegraphics[width=7cm]{../figures/example.pdf}
-	\caption{A simple, undirected graph $H$}\label{fig:graph}
+	\caption{A simple, undirected graph $G_1$}\label{fig:graph}
 \end{figure}
@@
 	\includegraphics[width=7cm]{../figures/example-vcp.pdf}
-	\caption{A minimum vertex coloring of $H$}\label{fig:vcp-example}
+	\caption{A minimum vertex coloring of $G_1$}\label{fig:vcp-example}
 \end{figure}
@@
 	\includegraphics[width=7cm]{../figures/example-cfcp.pdf}
-	\caption{A minimum conflict-free coloring of $H$}\label{fig:cfcp-example}
+	\caption{A minimum conflict-free coloring of $G_1$}\label{fig:cfcp-example}
 \end{figure}
@@
 This is because in a proper vertex coloring, every vertex is its own conflict-free neighbor \cite{abel2017three}.
-We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(H) = 3$ and $\chi_{CF}(H) = 2$.
+We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
 
@@
 The \emph{conflict-free domination number} for some $k$, denoted $\gamma_{CF}^k(G)$, is the minimum number of vertices that have to be colored in a conflict-free k-coloring of $G$.
-An example of a dominating set is $\{3, 5\}$ of graph $H$ where $\gamma(H) = 2$.
+An example of a dominating set is $\{3, 5\}$ of graph $G_1$ where $\gamma(G_1) = 2$.
 
@@
 
-As shown with graph $H$ in section \ref{sec:background}, even though all proper vertex colorings are also conflict-free colorings, fewer colors can usually be used.
+As shown with graph $G_1$ in section \ref{sec:background}, even though all proper vertex colorings are also conflict-free colorings, fewer colors can usually be used.
 This leads us to use heuristics that differ from the vertex coloring problem.
@@
 \subsection{Guaranteeing CF k-Colorability}
-It is wasteful to spend time coloring a graph that cannot be conflict-free colored with $k$ colors.
+It is wasteful to spend time coloring a graph that cannot be conflict-free colored.
 This leads Abel et al.
-\cite{abel2017three} to provide sufficient criterion to guarantee the conflict-free k-colorability of a graph.
-To introduce this criterion, we need to define a few more terms.
+to provide sufficient criterion to guarantee the conflict-free k-colorability of a certain graphs.
+To introduce this criterion, we need to introduce a few specific graphs.
+A complete graph is a simple, undirected graph where every pair of distinct vertices is connected by an edge.
+A complete graph on $n$ vertices is denoted as $K_n$.
+The graph $K_n^{-3}$ is the graph obtained by removing any three edges forming a single triangle, i.e.
+\(K_n^{-3} =  \left ( V(K_n), E(K_n) \setminus E(K_3) \right ) \).
+A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed from $G$ by deleting edges and vertices and by contracting edges.
+\cite{abel2017three,bondy1976graph}
+
+\begin{theorem} \label{thm:criterion}
+Let $G$ be a graph and $k \geq 1$.
+If $G$ has neither $K_{k+2}$ nor $K_{k+3}^{-3}$ as a minor, $G$ has a conflict-free coloring that can be found in polynomial time using iterated elimination of distance-3-sets.
+\end{theorem}
+
+Abel et al.
+give a criterion that guarantees k-colorability which is stated in theorem \ref{thm:criterion}.
+In the proof of this theorem, found in \cite{abel2017three}, the authors prove that their heuristic will always generate a k-colorable graph when the specified criterion is met.
+To illustrate this heuristic, we will generate a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined as algorithm \ref{alg:elimination}.
+
+% %%%%% REMOVE
+% \newpage
+% %%%%%
+
+\subsection{Setting Up Example CF Coloring}
+We will demonstrate meeting the criterion to utilize this algorithm using the graph $G_2$ in figure \ref{fig:criterion}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/criterion.pdf}
+	\caption{A simple graph $G_2$}\label{fig:criterion}
+\end{figure}
+
+We will be focusing on the simplest example, $k = 1$.
+Graph $G_2$ is a simple graph with 6 vertices.
+It does not, however, fit our criterion; it actually breaks both properties as it has both $K_{k+2}$ and $K_{k+4}^{-3}$ as a minor.
+For $k = 1$, this means our graph cannot contain $K_{3}$ or $K_{4}^{-3}$ as a minor.
+These graphs are shown in figure \ref{fig:bad-criterion}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/bad-criterion.pdf}
+	\caption{Graphs $K_{3}$ and $K_{4}^{-3}$, respectively}\label{fig:bad-criterion}
+\end{figure}
+
+We can see that $G_2$ has both of these as minors.
+The transformation needed to see the minors is shown in figure \ref{fig:criterion-minor}.
+By contracting the dotted edges, vertices 1 and 4 would combine as well as vertices 3 and 5.
+We would have both $K_{3}$ and $K_{4}^{-3}$.
+Thus, this graph cannot be conflict-free colored with one color.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/criterion-minor.pdf}
+	\caption{How to transform $G_2$ to see the minors}\label{fig:criterion-minor}
+\end{figure}
 
@@
 \section{Acknowledgments}
-\cite{abel2017three}
+Thanks to Peter Dolan and Elena Machkasova for their feedback on this paper.
 

### 2017-03-21 paper/paper.tex
Adding applications section

@@
 
+\section{Applications}
+Before digging into methods for solving the conflict-free coloring problem, it is important to understand why conflict-free coloring is useful.
+It is useful to know what motivated the recent studies into conflict-free coloring.
+
+\subsection{Wireless Networks}
+The main application for conflict-free coloring surrounds wireless networks.
+Cellular networks, radio, television broadcasting, and satellite communication utilize some form of wireless networks.
+For each of these systems, a frequency assignment problem arises with specific characteristics.
+
+For example, imagine a cellular network.
+Cellular networks are heterogeneous networks with two different types of nodes.
+They have \emph{base-stations} (servers) and \emph{clients}.
+Base stations are all interconnected through an external backbone network.
+Clients can only be connected to base stations and connect via radio links.
+Base stations are each assigned a fixed frequency.
+Clients, however, are constantly searching frequencies in search for base-stations with good reception.
+
+The problem when initially setting up these networks comes into play when assigning frequencies.
+Imagine two base-stations near each other having the same frequency.
+If a client is in reception range of both base-stations, then mutual interference occurs and the radio link is too noisy to be used for proper communication.
+The goal is to assign frequencies to base stations such that every client is served by some base-station and to minimize the number of frequencies used.
+
+This problem was initially modeled as a vertex coloring problem, where the vertices are the base-stations and the edges are the pairs of base-stations that overlap in their reception range.
+This model is too wasteful and restrictive.
+Imagine a situation where a client is within the reception range of 4 base-stations.
+The VCP model would require 4 colors, one for each base station.
+If we assign one base-station a color (say red) and the other 3 (say blue), then we only utilize two colors and the client utilizes the red base-station and has no mutual interference.
+This is exactly what a conflict-free coloring does.
+\cite{smorodinsky2013conflict}
+
 \section{CF Coloring of General Graphs}
@@
 To illustrate this heuristic, we will generate a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined as algorithm \ref{alg:elimination}.
-
-% %%%%% REMOVE
-% \newpage
-% %%%%%
 

### 2017-03-21 paper/paper.tex
Adding RFID application and some figures

@@
 Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one uniquely colored vertex.
+
+This paper looks into some applications and heuristics of conflict-free coloring.
+We then look into the specific case of conflict-free coloring planar graphs.
+Section 2 provides background necessary to understand the problem and how it is used.
+Section 3 introduces some applications for the conflict-free coloring problem.
+Section 4 describes a heuristic for conflict-free coloring general graphs.
+Section 5 looks into the specific case of conflict-free coloring planar graphs.
 
@@
 This model is too wasteful and restrictive.
-Imagine a situation where a client is within the reception range of 4 base-stations.
-The VCP model would require 4 colors, one for each base station.
-If we assign one base-station a color (say red) and the other 3 (say blue), then we only utilize two colors and the client utilizes the red base-station and has no mutual interference.
+Imagine a situation where a client is within the reception range of 3 base-stations.
+The VCP model would require 3 colors, one for each base station.
+If we assign one base-station a color (say blue) and the other 2 (say red), then we only utilize two colors and the client utilizes the blue base-station and has no mutual interference.
+This model is shown in figure \ref{fig:towers}.
 This is exactly what a conflict-free coloring does.
 \cite{smorodinsky2013conflict}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
+	\caption{Cellular tower VCP and CFCP example}\label{fig:towers}
+\end{figure}
+
+\subsection{RFID Networks}
+Radio frequency identification (RFID) networks are similar to wireless networks.
+An object, such as a credit card with an RFID chip, has a specific tag attached to it.
+A reader, such as a credit card scanner, can sense the presence of this object and read an ID that is assigned to the tag of the object.
+RFID is used for tracking progress of automobiles through a production assembly line, timing marathons and races, security access control to parking garages and buildings, and much more.
+
+Multiple RFID readers are often setup in a given location to improve coverage of the overall area.
+There can also be multiple RFID readers set up that each do a different action after reading a tagged object.
+Unlike cellular towers, a reader can only be reading (i.e.
+connected to) a single tag at a time.
+Two readers trying to access a tagged object at the same time can cause mutual interference.
+The goal is to schedule for each reader a time slot for when the reader will be active.
+
+Imagine we have a set of readers, $R$.
+Suppose they all are assigned the same frequency.
+We would like to schedule each reader $r \in R$ a time slot $t(r)$ where the reader $r$ will be active.
+We have a set of tags $P$ (i.e.
+automobile RFID chips).
+We can say that $P$ is read by our schedule if for every tag $p \in P$, there is at least one reader $r \in R$ and a time $t$ such that $p$ is read by $r$ at time $t$.
+We want to minimize the total time slots used by the schedule.
+This can be accomplished by modeling the situation as a conflict-free coloring problem.
+Again, we aim to find the minimum number of colors needed.
 

### 2017-03-21 paper/paper.tex
Adding some citations
Adding some stuff on planar graphs

@@
 Again, we aim to find the minimum number of colors needed.
+\cite{cheilaris2014strong, smorodinsky2013conflict}
 
@@
 \subsection{Iterated Elimination of Distance-3-Sets}
+The iterated elimination of distance-3-sets algorithm is a polynomial time heuristic for generating a conflict-free k-coloring of general graphs that meet the criterion in theorem \ref{thm:criterion}.
 
@@
 
+\todo[inline]{Create and go through an example of this algorithm}
+
 \section{CF Coloring of Planar Graphs}
+Conflict-free coloring has some interesting properties when we limit the input graph to be a planar graph.
+Recall that a graph is planar if it can be drawn on the plane in such a way that its edge intersect only at their endpoints.
 
-\section{Complexity of Coloring CF Graphs}
+\subsection{CF Four Color Theorem}
+Recall the map of the USA example given in the introduction.
+This is an example of a planar graph and has a famous theorem associated with it.
+We present this in theorem \ref{thm:four}.
+This theorem has been proved by multiple groups.
+The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.
+
+\begin{theorem} \label{thm:four}
+Every loopless planar graph admits a vertex coloring with at most four distinct colors
+\end{theorem}
+
+The conflict-free variation of this theorem is quite simple. We present this in theorem \ref{thm:four-cf}. It is given and proven in \cite{abel2017three}.
+
+\begin{theorem} \label{thm:four-cf}
+Every loopless planar graph admits a conflict-free coloring with at most three distinct colors
+\end{theorem}
+
+This can be easily thought of intuitively as we can take any four-colored planar graph and uncolor all vertices of a chosen color.
+This leaves us with some vertices uncolored and vertices colored with 3 other colors.
+Thus, it is always true that a planar graph can be conflict-free colored with 3 colors or less.
+An example of this is shown in figure \ref{fig:four}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/four.pdf}
+	\caption{A vertex coloring and CF coloring, respectively}\label{fig:four}
+\end{figure}
+
+\todo[inline]{Go into more methods for planar graphs}
 

### 2017-03-27 presentation/presentation.tex
Starting slide deck

\documentclass[xcolor=dvipsnames,aspectratio=1610]{beamer}
\usepackage{graphicx}
\usetheme[numbering=counter, progressbar=frametitle, sectionpage=none]{metropolis}
\title{Conflict-Free Vertex Coloring of Planar Graphs}
\date{April 15, 2017}
\author{Shawn Seymour}

\begin{document}
  \maketitle
  \begin{frame}{Virtual Machines vs. Containers}
      \alert{Virtual machines} virtualize hardware and run a full operating system as a guest.
      \begin{itemize}
          \item Can be several gigabytes in size and take awhile to spin up.
      \end{itemize}
      \vspace{10px}

      \alert{Containers} virtualize an operating system where containers share the kernel of the host machine.
      \begin{itemize}
          \item Can be tens of megabytes and spin up instantly.
      \end{itemize}

  \end{frame}

\end{document}

### 2017-03-27 presentation/presentation.tex
Adding first few slides to slide deck

@@
 \documentclass[xcolor=dvipsnames,aspectratio=1610]{beamer}
+
 \usepackage{graphicx}
+\usepackage[scale=2]{ccicons}
+
 \usetheme[numbering=counter, progressbar=frametitle, sectionpage=none]{metropolis}
+\setbeamercolor{background canvas}{bg=white}
+
 \title{Conflict-Free Vertex Coloring of Planar Graphs}
@@
   \maketitle
-  \begin{frame}{Virtual Machines vs. Containers}
-      \alert{Virtual machines} virtualize hardware and run a full operating system as a guest.
+
+  \begin{frame}
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=14cm]{../figures/map-no-colors.pdf}
+    \end{figure}
+  \end{frame}
+
+  \begin{frame}
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=14cm]{../figures/map-colors.pdf}
+    \end{figure}
+  \end{frame}
+
+  \section*{Background}
+
+  \subsection*{Graph Theory}
+
+  \begin{frame}
+    \frametitle{Graph Theory}
+
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=8cm]{../figures/example.pdf}
+    \end{figure}
+
+    \vfill
+
     \begin{itemize}
-          \item Can be several gigabytes in size and take awhile to spin up.
+      \item A \textbf{graph} is a set of vertices \emph{V} and a set of edges \emph{E}.
+      \item The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$.
+      \item The \textbf{closed neighborhood} of $v$ includes the neighborhood of $v$ and $v$ itself.
     \end{itemize}
-      \vspace{10px}
+  \end{frame}
 
-      \alert{Containers} virtualize an operating system where containers share the kernel of the host machine.
+  \subsection*{Graph Coloring}
+
+  \begin{frame}
+    \frametitle{Vertex Coloring}
+
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=8cm]{../figures/example-vcp.pdf}
+    \end{figure}
+
+    \vfill
+
     \begin{itemize}
-          \item Can be tens of megabytes and spin up instantly.
+      \item A proper \textbf{vertex coloring} of a graph $G$ is an assignment of colors to each vertex such that no adjacent vertices share the same color.
+      \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
     \end{itemize}
+  \end{frame}
 
+  \begin{frame}
+    \frametitle{Conflict-Free Coloring}
+
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=8cm]{../figures/example-cfcp.pdf}
+    \end{figure}
+
+    \vfill
+
+    \begin{itemize}
+      \item A \textbf{conflict-free coloring} of a graph $G$ assigns one of $k$ colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
+      \item Every proper vertex coloring of $G$ is also a conflict-free coloring of $G$. This is because every vertex can be its own conflict-free neighbor.
+    \end{itemize}
+  \end{frame}
+
+  \begin{frame}[standout]
+    \centering
+    Thanks to Peter Dolan and Elena Machkasova for their advice and feedback.
+    \vfill
+    \href{https://github.com/devshawn/senior-seminar}{github.com/devshawn/senior-seminar}
+    \vfill
+    \ccbyncsa{}
   \end{frame}

### 2017-03-28 paper/paper.tex
Making changes based on faculty suggestions

@@
 The vertex coloring problem aims to find the minimum number of colors needed to color a graph such that no two adjacent vertices are colored with the same color.
-While some problems are relatively easy to solve, the vertex coloring problem is one of the most computationally complex problems in computer science and mathematics.
+While some problems are relatively easy to solve, the vertex coloring problem is one of the most computationally complex problems in computer science and mathematics \cite{bondy1976graph}.
 The vertex coloring problem has many real-world applications such as exam timetabling, register allocation, and the scheduling of taxis.
@@
 A graph, denoted $G=(V,E)$, is an ordered pair of two sets: a set of vertices $V$ and a set of edges $E$.
-Each edge consists of a pair of vertices from $V$.
-For example, $(u,w) \in E$ is an edge connecting vertices $u$ and $w$ where $u,w \in V$.
+Each edge consists of a set of two unordered vertices from $V$.
+For example, $\{u, w\} \in E$ is an edge connecting vertices $u$ and $w$ where $u,w \in V$.
 Vertices are adjacent if they are connected by an edge.
@@
 $|S|$, needed to properly color $G$.
-The \emph{vertex coloring} problem, when given a simple graph $G$, is to find $\chi(G)$.
+The \emph{vertex coloring} problem (VCP), when given a simple graph $G$, is to find $\chi(G)$.
 \cite{bondy1976graph}
@@
 A graph having $\chi(G) = k$ is said to be a \emph{k-chromatic} graph.
-The \emph{k-colorability} problem asks if a graph can be colored using $k$ colors.
+The \emph{k-colorability} problem (CFCP) asks if a graph can be colored using $k$ colors.
 This problem is a slightly easier problem than the vertex coloring problem as it is decision problem rather than an optimization problem.
@@
 
-A \emph{conflict-free coloring} of a graph assigns one of $k$ colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
 A \emph{conflict-free k-coloring} of a simple graph $G$ assigns one of $k$ different colors to a subset $S \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the closed neighborhood of $v$.
+Generally, a \emph{conflict-free coloring} of a graph assigns colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
 The vertex $u$ can be thought of the \emph{conflict-free neighbor} of $v$.
@@
 
+A dominating set is a subset $D$ of $V$ such that every vertex not in $D$ is adjacent to at least one vertex in $D$.
 The domination number of $G$, denoted $\gamma(G)$, is the size of a minimum dominating set of G.
-A dominating set is a subset $D$ of $V$ such that every vertex not in $D$ is adjacent to at least one vertex in $D$.
 The \emph{conflict-free domination number} for some $k$, denoted $\gamma_{CF}^k(G)$, is the minimum number of vertices that have to be colored in a conflict-free k-coloring of $G$.
@@
 
-Given a decision problem and information showing what the answer is, it can be possible to verify the answer quickly.
+Given a decision problem and a proposed solution, it can be possible to verify the answer quickly.
 If a decision problem can be verified in polynomial time but not necessarily solved in polynomial time, it is said to be in the class \emph{NP}.
-Take note that this does not exclude problems in class \emph{P}; \emph{P} is a subset of \emph{NP}.
+Take note that this does not exclude problems in class P; P is a subset of NP.
 
-There are certain problems that can be proven to be as hard as every problem in NP.
-There problems are said to be NP-hard.
+There are certain problems, called NP-hard, that can be proven to be as hard as every problem in NP.
 A problem is NP-hard if it every problem in NP can be polynomially reduced to it.
-This brings an important result: if an NP-hard problem can be solved with an algorithm that runs in polynomial time, then any problem in NP could be solved in polynomial time.
+This means that if an NP-hard problem can be solved with a polynomial-time algorithm, then any problem in NP could be solved in polynomial time.
 A decision problem is said to be \emph{NP-complete} when it is both in NP and NP-hard.
 
-The vertex coloring problem (VCP) and the conflict-free coloring problem (CFCP) are not in the class NP as they are not decision problems.
-A common approach to proving problems as NP-hard or NP-complete is a reduction from a known NP problem.
-If we find a known hard problem $Y$, then we can prove that another problem $X$ is hard by reducing $Y$ to $X$.
+The k-colorability problem and the conflict-free k-colorability problem are NP-complete.
+This can be proven by using a reduction from a known NP-complete problem.
+If we find a known hard problem $Y$, we can prove that another problem $X$ is hard by a reduction from $Y$ to $X$.
 The VCP and the CFCP have both been shown to be NP-hard \cite{abel2017three,moret1998theory}.
@@
 \(K_n^{-3} =  \left ( V(K_n), E(K_n) \setminus E(K_3) \right ) \).
-A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed from $G$ by deleting edges and vertices and by contracting edges.
+A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed by contracting edges, deleting edges, or deleting vertices.
 \cite{abel2017three,bondy1976graph}
@@
 	\ForAll{components of $G$}
-		\State Pick a vertex $v$ and add it to $D$
+		\State Pick any vertex $v$
+		\State $D \gets D \cup \{ v \}$
 		\While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}

### 2017-03-29 paper/paper.tex
Trying changes in algorithm
Adding example for algorithm 1

@@
 Unless stated otherwise, we will assume when talking about neighborhoods that they are closed neighborhoods.
-The degree of a vertex, denoted $d_G(v)$, is the number of vertices adjacent to $v$.
-The maximum degree of a graph $G$, denoted $\Delta(G)$, is the maximum degree of its vertices.
+A path is a sequence of edges that connect a sequence of distinct vertices.
+A component of a graph $G$ is a subgraph $H$ where $H$ is connected and $H$ is not contained in any connected subgraph of $G$ that has more vertices or edges than $H$ has.
+An isolated path is a component that is itself a path.
 \cite{bondy1976graph}
@@
 \subsection{Iterated Elimination of Distance-3-Sets}
-The iterated elimination of distance-3-sets algorithm is a polynomial time heuristic for generating a conflict-free k-coloring of general graphs that meet the criterion in theorem \ref{thm:criterion}.
+The iterated elimination of distance-3-sets algorithm is a polynomial-time heuristic for generating a conflict-free coloring of general graphs that meet the criterion in theorem \ref{thm:criterion}.
 
@@
 \begin{algorithmic}[1]
-\State $i \gets 1$, $\chi \gets \emptyset$
+\State $i \gets 1$
 \State Remove all isolated paths from $G$
@@
 		\State $i \gets i + 1$
-		\State Remove $N[D]$ from $G$
+		\ForAll{$u \in D$}
+			\State Remove $N[u]$ from $G$
+		\EndFor
 		\State Remove all isolated paths from G
@@
 
-\todo[inline]{Create and go through an example of this algorithm}
+To illustrate this algorithm and show it produces a valid conflict-free coloring, we'll use graph $G_3$ shown in figure \ref{fig:algorithm1}.
+The algorithm starts by setting a variable $i$, the current color, to a (color) 1.
+We then remove all isolated paths from the input graph.
+There are currently no isolated paths in $G_3$, so we do not remove anything.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm1.pdf}
+	\caption{Graph $G_3$ to illustrate algorithm \ref{alg:elimination}}\label{fig:algorithm1}
+\end{figure}
+
+Since $G_3$ is not empty, we enter the first $while$ loop and set a variable $D$ to the empty set.
+$G_3$ has only one component (the whole graph) so we will only iterate through the $for\ all$ on line 5 once.
+Pick any vertex from $G_3$, say vertex 8.
+We then add 8 to set $D$ and thus $D \gets \{8\}$.
+Now, while there exists a vertex with a distance of at least 3 from all vertices in $D$, we must pick a vertex of exactly distance 3 and add it to $D$.
+For example, vertex 2 has distance 3 from vertex 8.
+Now, we add vertex 2 to $D$ and now $D \gets \{2, 8\}$.
+
+There are no more vertices of at least distance 3 from all vertices in $D$, so we move on to line 11.
+We color all vertices in $D$, $\{2,8\}$, with color $i$ which is known as color 1 (say red).
+This coloring is shown in figure \ref{fig:algorithm1-step1}.
+We increase $i$ by one leading to $i \gets 2$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm1-step1.pdf}
+	\caption{Graph $G_3$ after lines 1-13}\label{fig:algorithm1-step1}
+\end{figure}
+
+Next, for every vertex in $D$, we must remove their closed neighborhood from the graph.
+The neighborhood of vertex 2 consists of $\{1,2,3,6\}$ and the neighborhood of vertex 8 consists of $\{4,8\}$.
+By removing these vertices and any edges containing these vertices, we are left with vertices $\{5, 7\}$.
+This is shown in figure \ref{fig:algorithm1-step2}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=5cm]{../figures/algorithm1-step2.pdf}
+	\caption{Graph $G_3$ after lines 14-15}\label{fig:algorithm1-step2}
+\end{figure}
+
+The last step of the algorithm is to remove all isolated paths from $G$.
+Since we are left with only two vertices with no edges connecting them, we have 2 isolated paths.
+We remove these isolated paths from $G$ and are left with an empty graph.
+Since the graph is empty, we exit the outer $while$ loop and execute line 17.
+We color all removed isolated paths using color $i$, which is color 2 (say blue).
+Since we had 2 isolated paths, which are really just two vertices 5 and 7, we color each vertex with color 2.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm1-step3.pdf}
+	\caption{Graph $G_3$ after completing the algorithm}\label{fig:algorithm1-step3}
+\end{figure}
+
+It was easy to color our removed isolated paths as they consisted solely of a vertex.
+In a more complex example, an isolated path is colored by coloring the middle vertex of every three vertices.
+\cite{abel2017three}.
 
@@
 \section{Acknowledgments}
-Thanks to Peter Dolan and Elena Machkasova for their feedback on this paper.
+Thanks to Peter Dolan, Elena Machkasova, and Peh Ng for their advice and feedback.
 

### 2017-04-03 paper/paper.tex
Making progress on paper...

@@
 \alignauthor
-Shawn S. Seymour\\
+Shawn Seymour\\
 	\affaddr{Division of Science and Mathematics}\\
@@
 The conflict-free coloring problem is a variation of the vertex coloring problem, a classical NP-hard optimization problem.
-The conflict-free coloring problem aims to color the vertices of a graph in a way where every vertex is connected to at least one uniquely colored vertex.
-This paper presents heuristics to solve the conflict-free coloring problem on both general graphs and planar graphs.
-This paper also looks into bounds on the number of colors needed.
+The conflict-free coloring problem aims to color a possibly proper subset of vertices such that there is a unique color within the closed neighborhood (a vertex and its neighbors) of every vertex.
+This paper presents recent heuristics to solve the conflict-free coloring problem on both general graphs and planar graphs.
 \end{abstract}
@@
 We can represent each state with a \emph{vertex} and represent a boundary between two states with an \emph{edge}.
-This map is an example of a planar graph, i.e.
-none of the edges cross when drawn on a plane.
 
@@
 We then look into the specific case of conflict-free coloring planar graphs.
-Section 2 provides background necessary to understand the problem and how it is used.
+Section 2 provides the background necessary to understand the problem and how it is used.
 Section 3 introduces some applications for the conflict-free coloring problem.
@@
 The neighborhood of a vertex, denoted $N_G(v)$, is a set of all vertices adjacent to $v$.
-A \emph{closed} neighborhood consists of all vertices adjacent to $v$ and $v$ itself.
-Unless stated otherwise, we will assume when talking about neighborhoods that they are closed neighborhoods.
+A \emph{closed} neighborhood consists the vertices adjacent to $v$ plus $v$ itself.
+Unless stated otherwise, we will assume when writing about neighborhoods that they are closed neighborhoods.
+For example, let's examine $N_{G_1}(1)$ from figure  \ref{fig:graph}.
+The open neighborhood of 1 is $\{2, 5\}$ while the closed neighborhood is $\{1, 2, 5\}$.
+
 A path is a sequence of edges that connect a sequence of distinct vertices.
@@
 An isolated path is a component that is itself a path.
-\cite{bondy1976graph}
+
+A planar graph is a graph that can be drawn on the plane such that its edges only intersect at their endpoints.
+This drawing is referred to as a planar drawing.
+An outerplanar graph is a graph that has a planar drawing where every vertex belongs to the outer face of the drawing.
+\cite{bondy1976graph,west2001introduction}
 
@@
 \end{figure}
-
-\todo[inline]{The figures will be shaded with angled lines eventually}
 
@@
 An example of a conflict-free coloring is shown in figure \ref{fig:cfcp-example}.
+We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
 It is worth noting that all proper vertex colorings are also conflict-free colorings.
 This is because in a proper vertex coloring, every vertex is its own conflict-free neighbor \cite{abel2017three}.
-We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
 
@@
 
-Multiple RFID readers are often setup in a given location to improve coverage of the overall area.
+Multiple RFID readers are often set up in a given location to improve coverage of the overall area.
 There can also be multiple RFID readers set up that each do a different action after reading a tagged object.
@@
 \section{CF Coloring of General Graphs}
-For the rest of this paper, we will consider the NP-complete problem of conflict-free k-colorability.
+\label{sec:general-coloring}
+For this section, we will consider the NP-complete problem of conflict-free k-colorability.
 Given a graph $G$ and an integer $k$, determine if graph $G$ can be colored using $k$ or fewer colors.
@@
 \subsection{Iterated Elimination of Distance-3-Sets}
-The iterated elimination of distance-3-sets algorithm is a polynomial-time heuristic for generating a conflict-free coloring of general graphs that meet the criterion in theorem \ref{thm:criterion}.
+The iterated elimination of distance-3-sets algorithm is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in theorem \ref{thm:criterion}.
+If the criterion is not met, the heuristic will not generate a valid conflict-free k-coloring.
 
@@
 It was easy to color our removed isolated paths as they consisted solely of a vertex.
-In a more complex example, an isolated path is colored by coloring the middle vertex of every three vertices.
-\cite{abel2017three}.
+In a more complex example, an isolated path is colored by coloring the middle vertex of every three vertices \cite{abel2017three}.
+This graph is not 1-colorable as it includes $K_3$ as a minor.
+As we have shown that this graph is 2-colorable and know it is not 1-colorable, we can conclude that $\chi_{CF}(G_3) = 2$.
+
+It is wise to note that this algorithm does not minimize the number of colored vertices.
+It can be beneficial to minimize the number of colored vertices (less cost) in certain applications such as building wireless networks.
+The conflict-free domination number for $k=2$, $\gamma_{CF}^2(G_3)$, is three even though we have four colored vertices in our example.
 
 \section{CF Coloring of Planar Graphs}
+\label{sec:planar-coloring}
 Conflict-free coloring has some interesting properties when we limit the input graph to be a planar graph.
@@
 
-\subsection{CF Four Color Theorem}
+\subsection{Bounds for Planar Graphs}
+\label{sec:bounds}
 Recall the map of the USA example given in the introduction.
-This is an example of a planar graph and has a famous theorem associated with it.
-We present this in theorem \ref{thm:four}.
-This theorem has been proved by multiple groups.
+This is an example of a planar graph and illustrates a famous theorem associated with it.
+We present this theorem, called the four color theorem, in theorem \ref{thm:four}.
+It has been proved by multiple groups.
 The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.
@@
 
-The conflict-free variation of this theorem is quite simple. We present this in theorem \ref{thm:four-cf}. It is given and proven in \cite{abel2017three}.
+Due to theorem \ref{thm:four}, we immediately know that every planar graph is 4-colorable.
+This raises the question of whether there are planar graphs that require four colors or if fewer colors could suffice for all planar graphs.
+This leads us to the conflict-free variation of this theorem.
+We present this in theorem \ref{thm:four-cf}.
+It is given and proven in \cite{abel2017three}.
+In the next subsections, we will investigate this result.
 
@@
 
-This can be easily thought of intuitively as we can take any four-colored planar graph and uncolor all vertices of a chosen color.
-This leaves us with some vertices uncolored and vertices colored with 3 other colors.
-Thus, it is always true that a planar graph can be conflict-free colored with 3 colors or less.
-An example of this is shown in figure \ref{fig:four}.
-
 \begin{figure}[h]
@@
 	\includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/four.pdf}
-	\caption{A vertex coloring and CF coloring, respectively}\label{fig:four}
+	\caption{A vertex and CF coloring, respectively}\label{fig:four}
 \end{figure}
 
-\todo[inline]{Go into more methods for planar graphs}
+Figure \ref{fig:four} looks at a planar graph that requires four colors in a proper vertex coloring.
+Based on theorem \ref{thm:four-cf}, we know that this planar graph can be conflict-free colored with only three colors.
+
+\subsection{Outerplanar Graphs}
+
+\subsection{Planar Graphs}
+As stated in theorem \ref{thm:four-cf} in section \ref{sec:bounds}, all planar graphs are 3-colorable.
 
@@
 \label{sec:conclusion}
+I have presented some of the recent heuristics and findings on the conflict-free coloring problem.
+Although the CFCP is NP-hard and finding the minimum number colors needed requires inefficient brute force algorithms, there are heuristics to find good conflict-free colorings.
+It is still a recent problem in the world of computer science and mathematics, so research is still being conducted and proofs results are being presented.
+
+There are many applications of the CFCP that benefit from the recent research into the field.
+It is easier to minimize frequency assignment for wireless networks and model RFID networks.
+Current research focuses on finding bounds and properties on specific cases such as planar graphs, interval graphs, types of hypergraphs, and more.
+There is also recent interest in variations of the CFCP such as requiring \emph{another} vertex (not the selected vertex) to be colored within the neighborhood of a selected vertex.
+This allows for applications such as guiding a specific robot to other locations (i.e.
+the robot and its destination would both be a distinct unique color).
 

### 2017-04-03 paper/paper.tex
Making progress towards six pages

@@
 \newtheorem{theorem}{Theorem}
+
+\algnewcommand\algorithmicinput{\textbf{Input:}}
+\algnewcommand\Input{\item[\algorithmicinput]}
 
@@
 An example of a dominating set is $\{3, 5\}$ of graph $G_1$ where $\gamma(G_1) = 2$.
+The \emph{k-conflict-free dominating set} problem asks if a given k-coloring of a graph colors the minimum amount of vertices needed to have a coloring that utilizes $k$ colors.
 
@@
 The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, a well-known NP-complete problem \cite{sharma2012new}.
+
+It is often desirable and necessary to use approximation algorithms, known as heuristics, to solve complex problems like the VCP and the CFCP.
+In our case, heuristics are polynomial-time algorithms that give good, but not optimal, solutions to our optimization problems.
+A polynomial-time approximation scheme (PTAS) is any polynomial-time approximation algorithm that takes an instance of an optimization problem and a parameter $\epsilon > 0$ and produces a solution that is within a factor $(1 + \epsilon)$ (for minimization problems) of being optimal.
 
@@
 In the proof of this theorem, found in \cite{abel2017three}, the authors prove that their heuristic will always generate a k-colorable graph when the specified criterion is met.
-To illustrate this heuristic, we will generate a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined as algorithm \ref{alg:elimination}.
+To illustrate this heuristic, we will generate a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined in algorithm \ref{alg:elimination}.
 
@@
 \begin{theorem} \label{thm:four}
-Every loopless planar graph admits a vertex coloring with at most four distinct colors
+Every loopless planar graph admits a vertex coloring with at most four distinct colors.
 \end{theorem}
@@
 \begin{theorem} \label{thm:four-cf}
-Every loopless planar graph admits a conflict-free coloring with at most three distinct colors
+Every loopless planar graph admits a conflict-free coloring with at most three distinct colors.
 \end{theorem}
@@
 
-\subsection{Outerplanar Graphs}
+\subsection{One or Two Colors}
+\todo[inline]{To do still....}
 
-\subsection{Planar Graphs}
-As stated in theorem \ref{thm:four-cf} in section \ref{sec:bounds}, all planar graphs are 3-colorable.
+\subsection{Three or More Colors}
+Abel et.
+al \cite{abel2017three} present specific results for 3-colorable graphs.
+They examine minimizing the number of colored vertices of 3-colorable graphs.
+They prove theorems \ref{thm:approximate-cfds} and \ref{thm:outerplanar-cfdn} by using a polynomial-time algorithm that transforms a dominating set $D$ of a planar graph $G$ into a conflict-free k-coloring of $G$ where only the vertices of $D$ are colored.
+This algorithm is defined in algorithm \ref{alg:cf-dominating}.
+
+\begin{algorithm}
+\caption{Conflict-Free Coloring via Dominating Set} \label{alg:cf-dominating}
+\begin{algorithmic}[1]
+\Input A planar graph $G = (V, E)$
+\State Find a dominating set of $G$
+\While{$V \setminus D \neq \emptyset$}
+	\ForAll{$v \in V \setminus D$}
+		\State Pick a vertex $u \in D$
+		\State Contract the edge $\{u,v\}$ towards $u$
+	\EndFor
+\EndWhile
+\State Find a proper vertex coloring of $G$
+\end{algorithmic}
+\end{algorithm}
+
+%To prove theorem \ref{thm:approximate-cfds}, we use a reduction from \emph{k-coloring} to \emph{conflict-free k-coloring}.
+This reduction is out of the scope of this paper and can be found in \cite{abel2017three}.
+The reduction preserves the planarity of its input graph, so the resulting graph is still planar.
+We also know that 3-coloring a graph is NP-complete \cite{sharma2012new}.
+
+Because the planar minimum dominating set problem is NP-hard \cite{garey2002computers}, we know that the conflict-free dominating set problem is NP-hard because we are finding a minimum dominating set.
+It follows that the corresponding decision problem, the k-conflict-free dominating set problem, is NP-complete.
+
+\begin{theorem} \label{thm:approximate-cfds}
+For $k \geq 4$, the k-conflict-free dominating set problem is NP-complete and $\gamma_{CF}^k(G) = \gamma(G)$ for a planar graph $G$. Also, there exists a PTAS for estimating $\gamma_{CF}^k(G)$.
+\end{theorem}
+
+We get a PTAS for the conflict-free domination number by applying algorithm \ref{alg:cf-dominating} and finding the dominating set using the PTAS defined by Baker and Hill \cite{baker1994approximation}.
+As the input graph $G$ is planar, the resulting graph $G'$ is also planar because $G'$ is a minor of $G$.
+Thus, it can be colored with 4 colors by \ref{thm:four}.
+We then color $G$ with the colors of $G'$, leaving any vertex in $G$ but not in $G'$ uncolored.
+This leaves us with a conflict-free 4-coloring of $G$.
+Note that it has a minimal number of vertices colored because we used a PTAS to find the minimum dominating set.
+
+\begin{theorem} \label{thm:outerplanar-cfdn}
+If a graph $G$ is outerplanar, then $\gamma_{CF}^k(G) = \gamma(G)$. Also, there exists a linear-time algorithm to compute $\gamma_{CF}^k(G)$.
+\end{theorem}
 
@@
 Current research focuses on finding bounds and properties on specific cases such as planar graphs, interval graphs, types of hypergraphs, and more.
+
 There is also recent interest in variations of the CFCP such as requiring \emph{another} vertex (not the selected vertex) to be colored within the neighborhood of a selected vertex.

### 2017-04-03 paper/paper.tex
Six pages has arrived

@@
 The \emph{k-colorability} problem (CFCP) asks if a graph can be colored using $k$ colors.
-This problem is a slightly easier problem than the vertex coloring problem as it is decision problem rather than an optimization problem.
+This problem is slightly easier than the VCP as it is decision problem rather than an optimization problem.
 An example of a 3-colorable graph and a vertex coloring is shown in figure \ref{fig:vcp-example}.
@@
 
-A \emph{conflict-free k-coloring} of a simple graph $G$ assigns one of $k$ different colors to a subset $S \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the closed neighborhood of $v$.
+A \emph{conflict-free k-coloring} of a simple graph $G$ assigns one of $k$ different colors to a subset $P \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the closed neighborhood of $v$.
+The set $V \setminus S$ contains any uncolored vertices.
 Generally, a \emph{conflict-free coloring} of a graph assigns colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
@@
 \(K_n^{-3} =  \left ( V(K_n), E(K_n) \setminus E(K_3) \right ) \).
-A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed by contracting edges, deleting edges, or deleting vertices.
+A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed by deleting edges and/or contracting edges (combining the vertices of an edge) from $G$.
 \cite{abel2017three,bondy1976graph}
@@
 \subsection{Iterated Elimination of Distance-3-Sets}
+\label{sec:iterated}
 The iterated elimination of distance-3-sets algorithm is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in theorem \ref{thm:criterion}.
@@
 \begin{algorithmic}[1]
+\Input A simple, undirected graph $G$
 \State $i \gets 1$
@@
 	\includegraphics[width=6cm]{../figures/algorithm1-step3.pdf}
-	\caption{Graph $G_3$ after completing the algorithm}\label{fig:algorithm1-step3}
+	\caption{Coloring of $G_3$ based on algorithm}\label{fig:algorithm1-step3}
 \end{figure}
@@
 
-It is wise to note that this algorithm does not minimize the number of colored vertices.
+It is wise to note that this algorithm does not necessariyminimize the number of colored vertices.
 It can be beneficial to minimize the number of colored vertices (less cost) in certain applications such as building wireless networks.
-The conflict-free domination number for $k=2$, $\gamma_{CF}^2(G_3)$, is three even though we have four colored vertices in our example.
+The conflict-free domination number for $k=2$ of $G_3$, $\gamma_{CF}^2(G_3)$, is three even though we have four colored vertices in our example.
+This can be seen by coloring vertices $\{2, 8\}$ with one color and vertex 6 with another.
 
@@
 Conflict-free coloring has some interesting properties when we limit the input graph to be a planar graph.
-Recall that a graph is planar if it can be drawn on the plane in such a way that its edge intersect only at their endpoints.
+Recall that a graph is planar if it can be drawn on the plane in such a way that its edges intersect only at their endpoints.
 
@@
 We present this theorem, called the four color theorem, in theorem \ref{thm:four}.
-It has been proved by multiple groups.
+It has been proven by multiple groups.
 The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.
@@
 
-Due to theorem \ref{thm:four}, we immediately know that every planar graph is 4-colorable.
+Due to theorem \ref{thm:four}, we immediately know that every planar graph is conflict-free 4-colorable.
 This raises the question of whether there are planar graphs that require four colors or if fewer colors could suffice for all planar graphs.
@@
 It is given and proven in \cite{abel2017three}.
-In the next subsections, we will investigate this result.
 
@@
 
-\subsection{One or Two Colors}
-\todo[inline]{To do still....}
-
-\subsection{Three or More Colors}
+\subsection{Minimizing Colored Vertices}
 Abel et.
@@
 \Input A planar graph $G = (V, E)$
-\State Find a dominating set of $G$
-\While{$V \setminus D \neq \emptyset$}
+\State Find a dominating set, $D$, of $G$
 \ForAll{$v \in V \setminus D$}
-		\State Pick a vertex $u \in D$
+	\State Pick a vertex $u \in D$ where $\{u, v\} \in E$
 	\State Contract the edge $\{u,v\}$ towards $u$
 \EndFor
-\EndWhile
 \State Find a proper vertex coloring of $G$
+\State Color the original $G$ with the found coloring
 \end{algorithmic}
@@
 
-%To prove theorem \ref{thm:approximate-cfds}, we use a reduction from \emph{k-coloring} to \emph{conflict-free k-coloring}.
-This reduction is out of the scope of this paper and can be found in \cite{abel2017three}.
-The reduction preserves the planarity of its input graph, so the resulting graph is still planar.
-We also know that 3-coloring a graph is NP-complete \cite{sharma2012new}.
-
-Because the planar minimum dominating set problem is NP-hard \cite{garey2002computers}, we know that the conflict-free dominating set problem is NP-hard because we are finding a minimum dominating set.
+Because the planar minimum dominating set problem is NP-hard \cite{garey2002computers}, we know that the conflict-free dominating set problem is NP-hard because we aim to find a minimum dominating set.
 It follows that the corresponding decision problem, the k-conflict-free dominating set problem, is NP-complete.
@@
 This leaves us with a conflict-free 4-coloring of $G$.
-Note that it has a minimal number of vertices colored because we used a PTAS to find the minimum dominating set.
 
@@
 \end{theorem}
+
+\subsection{CF Coloring via Dominating Set}
+Algorithm \ref{alg:elimination} presented in section \ref{sec:iterated} gives us an efficient heuristic for coloring general graphs including planar graphs.
+Algorithm \ref{alg:cf-dominating} gives us another way of coloring planar graphs, albeit likely less efficient.
+
+To demonstrate this algorithm, we will utilize graph $G_3$ as we did for algorithm \ref{alg:elimination}.
+It is a planar graph, so we can use this algorithm to generate a conflict-free coloring.
+First, we must find a dominating set for $G_3$.
+Finding a dominating set can be done with a greedy algorithm.
+For small graphs, such as $G_3$, it is easy to find one by hand.
+A dominating set of $G_3, \{2, 6, 8\},$ is shown in figure \ref{fig:algorithm2-step1}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm2-step1.pdf}
+	\caption{A dominating set of $G_3$}\label{fig:algorithm2-step1}
+\end{figure}
+
+We assign our dominating set $\{2,6,8\}$ to $D$.
+Since $V \setminus D \neq \emptyset$, we enter the \emph{for all} loop in line 2.
+Here, we iterate through all vertices in $V \setminus D$.
+For each vertex $v \in V \setminus D$, we will pick another vertex in $D$ that is connected to $v$ by an edge.
+Then, we will contract the edge $\{u, v\}$ towards $u$.
+This means that we combine $u$ and $v$ together and update any edges to reflect the changes.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm2-step2.pdf}
+	\caption{The graph after the first \emph{for} loop}\label{fig:algorithm2-step2}
+\end{figure}
+
+To illustrate this, we start the loop by picking a vertex $v$, say vertex 3.
+We pick vertex $u$ to be vertex 2 because $2 \in D$ and $\{2, 3\} \in E$.
+We contract the edge and show the resulting graph $G$ in figure \ref{fig:algorithm2-step2}.
+By iterating over the rest of the vertices in $V \setminus D$, we obtain a graph that is itself a path from vertex 2 to vertex 6 to vertex 8.
+This graph, along with its proper vertex coloring, is shown in figure \ref{fig:algorithm2-step3}.
+We can find a proper vertex coloring by any heuristic, such as a greedy algorithm, for the VCP.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=5cm]{../figures/algorithm2-step3.pdf}
+	\caption{The graph after lines 2-5}\label{fig:algorithm2-step3}
+\end{figure}
+
+Lastly, we color our original graph $G_3$ based on the proper vertex coloring we generated.
+We leave any nodes not in the graph $G$ uncolored when we color $G_3$.
+The coloring of $G_3$ is shown in figure \ref{fig:algorithm2-step4}.
+It is clear that this has produced a conflict-free coloring.
+Looking back at algorithm \ref{alg:elimination}, we had 4 colored vertices.
+Here, we have 3, and it is true that we have minimized colored vertices as $\gamma_{CF}^2(G_3) = 3$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm2-step4.pdf}
+	\caption{$G_3$ with minimized colored vertices}\label{fig:algorithm2-step4}
+\end{figure}
 
@@
 
-There are many applications of the CFCP that benefit from the recent research into the field.
-It is easier to minimize frequency assignment for wireless networks and model RFID networks.
+There are many applications of the CFCP that benefit from the recent research into conflict-free coloring.
+It is easier to minimize frequency assignment for wireless networks and design RFID networks.
 Current research focuses on finding bounds and properties on specific cases such as planar graphs, interval graphs, types of hypergraphs, and more.

### 2017-04-06 paper/paper.tex
Six-page draft so far...

@@
 The conflict-free coloring problem does not aim to color every vertex such that it is not connected to a vertex of the same color.
-Rather, it aims to color \emph{enough} vertices such that for every vertex, it is connected to at least one uniquely colored vertex.
+Rather, it aims to color \emph{enough} vertices such that for every vertex, there is a unique color assigned to a vertex within its closed neighborhood.
 
@@
 A simple graph is an undirected graph where each edge connects two different vertices and no two edges connect the same pair of vertices.
+A planar graph is a graph that can be drawn on the plane such that its edges only intersect at their endpoints.
+This drawing is referred to as a planar drawing.
 All graphs used by the vertex coloring problem and conflict-free coloring problem will be undirected, simple graphs.
@@
 
-A path is a sequence of edges that connect a sequence of distinct vertices.
+A \emph{path} is a sequence of edges that connect a sequence of distinct vertices.
 A component of a graph $G$ is a subgraph $H$ where $H$ is connected and $H$ is not contained in any connected subgraph of $G$ that has more vertices or edges than $H$ has.
@@
 
-A planar graph is a graph that can be drawn on the plane such that its edges only intersect at their endpoints.
-This drawing is referred to as a planar drawing.
-An outerplanar graph is a graph that has a planar drawing where every vertex belongs to the outer face of the drawing.
+The distance of a path can be thought of the smallest number of edges needed to be crossed to get from one vertex to another vertex.
+For example, in figure \ref{fig:graph}, the distance from vertex 3 to vertex 4 would be 3 as it takes 3 edges to get there.
+A \emph{distance-3-set} is a set of vertices that all have exactly distance 3 from each other.
+An example of a distance-3-set from figure \ref{fig:graph} would be $\{3,4\}$.
 \cite{bondy1976graph,west2001introduction}
@@
 An example of a conflict-free coloring is shown in figure \ref{fig:cfcp-example}.
+All uncolored vertices are in gray.
+It is a valid conflict-free coloring because every vertex has a unique color within its closed neighborhood.
+For example, $N(1) = \{1: uncolored,\ 2: uncolored,\ 5: red\}$.
+Thus, red is the unique color within the closed neighborhood of vertex 1.
 We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
@@
 A \emph{decision} problem, as mentioned earlier, is a problem that can be answered with a `yes' or a `no' \cite{sipser2006introduction}.
+A problem can be solved in polynomial time if an algorithm with input size $n$ can run in at most $n^k$ steps where $k$ is a constant that does not depend on $n$.
 A decision problem is said to be in the class \emph{P} if in the worst case, it can be solved with an algorithm that runs in polynomial time.
-A problem can be solved in polynomial time if an algorithm with input size $n$ can run in at most $n^k$ steps where $k$ is a constant that does not depend on $n$.
 
@@
 There are certain problems, called NP-hard, that can be proven to be as hard as every problem in NP.
+If problem $Y$ can be transformed into problem $X$ by a polynomial-time algorithm, it is said that $Y$ can be polynomially reduced to $X$.
 A problem is NP-hard if it every problem in NP can be polynomially reduced to it.
@@
 \section{Applications}
-Before digging into methods for solving the conflict-free coloring problem, it is important to understand why conflict-free coloring is useful.
-It is useful to know what motivated the recent studies into conflict-free coloring.
+Before digging into methods for solving the CFCP, it is important to understand what motivated the recent studies into conflict-free coloring.
 
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
+	\caption{Cellular tower VCP and CFCP example}\label{fig:towers}
+\end{figure}
+
 This problem was initially modeled as a vertex coloring problem, where the vertices are the base-stations and the edges are the pairs of base-stations that overlap in their reception range.
@@
 \cite{smorodinsky2013conflict}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
-	\caption{Cellular tower VCP and CFCP example}\label{fig:towers}
-\end{figure}
 
@@
 		\ForAll{$u \in D$}
-			\State Remove $N[u]$ from $G$
+			\State Remove $N(u)$ from $G$
 		\EndFor
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=6cm]{../figures/algorithm1.pdf}
-	\caption{Graph $G_3$ to illustrate algorithm \ref{alg:elimination}}\label{fig:algorithm1}
-\end{figure}
-
 Since $G_3$ is not empty, we enter the first $while$ loop and set a variable $D$ to the empty set.
@@
 Now, we add vertex 2 to $D$ and now $D \gets \{2, 8\}$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=6cm]{../figures/algorithm1.pdf}
+	\caption{Graph $G_3$ to illustrate algorithm \ref{alg:elimination}}\label{fig:algorithm1}
+\end{figure}
 
@@
 
-It is wise to note that this algorithm does not necessariyminimize the number of colored vertices.
+It is wise to note that this algorithm does not necessarily minimize the number of colored vertices.
 It can be beneficial to minimize the number of colored vertices (less cost) in certain applications such as building wireless networks.
@@
 We present this theorem, called the four color theorem, in theorem \ref{thm:four}.
-It has been proven by multiple groups.
 The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.
@@
 
-\begin{theorem} \label{thm:four-cf}
-Every loopless planar graph admits a conflict-free coloring with at most three distinct colors.
-\end{theorem}
-
 \begin{figure}[h]
@@
 
+\begin{theorem} \label{thm:four-cf}
+Every loopless planar graph admits a conflict-free coloring with at most three distinct colors.
+\end{theorem}
+
 Figure \ref{fig:four} looks at a planar graph that requires four colors in a proper vertex coloring.
 Based on theorem \ref{thm:four-cf}, we know that this planar graph can be conflict-free colored with only three colors.
+This is shown in figure \ref{fig:four} as well.
 
-\subsection{Minimizing Colored Vertices}
-Abel et.
-al \cite{abel2017three} present specific results for 3-colorable graphs.
-They examine minimizing the number of colored vertices of 3-colorable graphs.
-They prove theorems \ref{thm:approximate-cfds} and \ref{thm:outerplanar-cfdn} by using a polynomial-time algorithm that transforms a dominating set $D$ of a planar graph $G$ into a conflict-free k-coloring of $G$ where only the vertices of $D$ are colored.
-This algorithm is defined in algorithm \ref{alg:cf-dominating}.
+\subsection{CF Coloring via Dominating Set}
+\label{sec:coloring-dom}
+Algorithm \ref{alg:elimination} presented in section \ref{sec:iterated} gives us an efficient heuristic for coloring general graphs including planar graphs.
+Algorithm \ref{alg:cf-dominating}, called conflict-free via dominating set, gives us another way of coloring planar graphs, albeit likely less efficient.
 
@@
 \end{algorithm}
-
-Because the planar minimum dominating set problem is NP-hard \cite{garey2002computers}, we know that the conflict-free dominating set problem is NP-hard because we aim to find a minimum dominating set.
-It follows that the corresponding decision problem, the k-conflict-free dominating set problem, is NP-complete.
-
-\begin{theorem} \label{thm:approximate-cfds}
-For $k \geq 4$, the k-conflict-free dominating set problem is NP-complete and $\gamma_{CF}^k(G) = \gamma(G)$ for a planar graph $G$. Also, there exists a PTAS for estimating $\gamma_{CF}^k(G)$.
-\end{theorem}
-
-We get a PTAS for the conflict-free domination number by applying algorithm \ref{alg:cf-dominating} and finding the dominating set using the PTAS defined by Baker and Hill \cite{baker1994approximation}.
-As the input graph $G$ is planar, the resulting graph $G'$ is also planar because $G'$ is a minor of $G$.
-Thus, it can be colored with 4 colors by \ref{thm:four}.
-We then color $G$ with the colors of $G'$, leaving any vertex in $G$ but not in $G'$ uncolored.
-This leaves us with a conflict-free 4-coloring of $G$.
-
-\begin{theorem} \label{thm:outerplanar-cfdn}
-If a graph $G$ is outerplanar, then $\gamma_{CF}^k(G) = \gamma(G)$. Also, there exists a linear-time algorithm to compute $\gamma_{CF}^k(G)$.
-\end{theorem}
-
-\subsection{CF Coloring via Dominating Set}
-Algorithm \ref{alg:elimination} presented in section \ref{sec:iterated} gives us an efficient heuristic for coloring general graphs including planar graphs.
-Algorithm \ref{alg:cf-dominating} gives us another way of coloring planar graphs, albeit likely less efficient.
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=6cm]{../figures/algorithm2-step2.pdf}
-	\caption{The graph after the first \emph{for} loop}\label{fig:algorithm2-step2}
-\end{figure}
-
 To illustrate this, we start the loop by picking a vertex $v$, say vertex 3.
@@
 	\centering
-	\includegraphics[width=5cm]{../figures/algorithm2-step3.pdf}
-	\caption{The graph after lines 2-5}\label{fig:algorithm2-step3}
+	\includegraphics[width=6cm]{../figures/algorithm2-step2.pdf}
+	\caption{The graph after the first \emph{for} loop}\label{fig:algorithm2-step2}
 \end{figure}
@@
 It is clear that this has produced a conflict-free coloring.
-Looking back at algorithm \ref{alg:elimination}, we had 4 colored vertices.
-Here, we have 3, and it is true that we have minimized colored vertices as $\gamma_{CF}^2(G_3) = 3$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=5cm]{../figures/algorithm2-step3.pdf}
+	\caption{The graph after lines 2-5}\label{fig:algorithm2-step3}
+\end{figure}
+
+Take note that this algorithm has produced fewer colored vertices than algorithm \ref{alg:elimination}.
+We had 4 colored vertices based on that algorithm where here we have 3.
+This algorithm helps us prove theorems based on minimizing the number of colored vertices.
 
@@
 \end{figure}
+
+\subsection{Minimizing Colored Vertices}
+Abel et.
+al \cite{abel2017three} present results on minimizing colored vertices when conflict-free coloring planar graphs.
+They propose and prove theorem \ref{thm:approximate-cfds} by using the polynomial-time algorithm described in algorithm \ref{alg:cf-dominating}.
+
+Because the planar minimum dominating set problem is NP-hard \cite{garey2002computers}, we know that the conflict-free dominating set problem is NP-hard because we aim to find a dominating set.
+It follows that the corresponding decision problem, the k-conflict-free dominating set problem, is NP-complete.
+
+\begin{theorem} \label{thm:approximate-cfds}
+For $k \geq 4$, the k-conflict-free dominating set problem is NP-complete and $\gamma_{CF}^k(G) = \gamma(G)$ for a planar graph $G$. Also, there exists a PTAS for estimating $\gamma_{CF}^k(G)$.
+\end{theorem}
+
+We get a PTAS for the conflict-free domination number by applying algorithm \ref{alg:cf-dominating} and finding the dominating set using the PTAS defined by Baker and Hill \cite{baker1994approximation}.
+As the input graph $G$ is planar, the resulting graph $G'$ is also planar because $G'$ is a minor of $G$.
+Thus, it can be colored with 4 colors or less by \ref{thm:four}.
+We then color $G$ with the colors of $G'$, leaving any vertex in $G$ but not in $G'$ uncolored.
+This leaves us with a conflict-free coloring of $G$.
 

### 2017-04-09 presentation/presentation.tex
Adding outline stuff
Adding neighborhood examples to presentation

@@
 \usepackage[scale=2]{ccicons}
+\usepackage{multicol}
+\usepackage[absolute,overlay]{textpos}
+% \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
+% {eso-pic}
+
+\newcommand{\exampleheight}{1.9cm}
+\newcommand{\examplewidth}{16cm}
 
@@
 
-  \section*{Background}
+  \begin{frame}
+    \frametitle{Overview}
+    \begin{multicols}{2}
+      \tableofcontents
+    \end{multicols}
+  \end{frame}
 
-  \subsection*{Graph Theory}
+  \section{Background}
+
+  \subsection{Graph Theory}
 
@@
 
-    \begin{figure}[h]
+    \only<1-2>{
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
         \centering
         \includegraphics[width=8cm]{../figures/example.pdf}
-    \end{figure}
+      \end{textblock*}
+    }
+
+    \only<3> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-neighborhoods-1.pdf}
+      \end{textblock*}
+    }
+
+    \only<4> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-neighborhoods-2.pdf}
+      \end{textblock*}
+    }
+
+    \vspace{4cm}
 
@@
     \begin{itemize}
-      \item A \textbf{graph} is a set of vertices \emph{V} and a set of edges \emph{E}.
-      \item The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$.
-      \item The \textbf{closed neighborhood} of $v$ includes the neighborhood of $v$ and $v$ itself.
+      \item<1-4> A \textbf{graph} is the set of vertices \emph{V} and a set of edges \emph{E}.
+      \item<2-4> The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$ plus $v$ itself.
+      \only<1-2>{\item<3> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
+      \only<3>{\item<3> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
+      \only<4>{\item<4> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
     \end{itemize}
+
   \end{frame}
 
-  \subsection*{Graph Coloring}
+  \subsection{Graph Coloring}
 
@@
 
-    \begin{figure}[h]
+    \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
       \centering
       \includegraphics[width=8cm]{../figures/example-vcp.pdf}
-    \end{figure}
+    \end{textblock*}
+
+    \vspace{4cm}
 
@@
 
-    \vfill
-
     \begin{itemize}
-      \item A \textbf{conflict-free coloring} of a graph $G$ assigns one of $k$ colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
+      \item A \textbf{conflict-free coloring} of a graph $G$ assigns colors to some vertices such that there is a uniquely colored vertex within the closed neighborhood of every vertex.
       \item Every proper vertex coloring of $G$ is also a conflict-free coloring of $G$. This is because every vertex can be its own conflict-free neighbor.
@@
 
+  \addtocontents{toc}{\protect\vspace{14pt}}
+
+  \section{Applications}
+
+  \subsection{Wireless Networks}
+
+  \subsection{RFID Networks}
+
+  \addtocontents{toc}{\newpage}
+
+  \section{CF Coloring for General Graphs}
+
+  \section{CF Coloring for Planar Graphs}
+
   \begin{frame}[standout]
     \centering
-    Thanks to Peter Dolan and Elena Machkasova for their advice and feedback.
+    {Thanks to Peter Dolan, Elena Machkasova,
+
+    and Peh Ng for their advice and feedback.}
     \vfill

### 2017-04-10 presentation/presentation.tex
Adding more CF coloring examples to presentation

@@
 \usepackage{multicol}
+\usepackage{enumitem}
+\usepackage{xcolor}
 \usepackage[absolute,overlay]{textpos}
@@
       \centering
-      \includegraphics[width=14cm]{../figures/map-no-colors.pdf}
+      \includegraphics[width=14cm]{../figures/map-no-colors-1.pdf}
     \end{figure}
@@
     \vspace{4cm}
-
     \vfill
@@
     \begin{itemize}
-      \item A proper \textbf{vertex coloring} of a graph $G$ is an assignment of colors to each vertex such that no adjacent vertices share the same color.
+      \item A proper \textbf{vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
       \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
@@
 
+    \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+      \centering
+      \includegraphics[width=8cm]{../figures/example-cfcp.pdf}
+    \end{textblock*}
+
+    \vspace{4cm}
+    \vfill
+
+    \begin{itemize}
+      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that there is a uniquely colored vertex within the neighborhood of every vertex.
+      \item<2> Every proper vertex coloring of $G$ is also a conflict-free coloring of $G$ as every vertex $v$ would be a unique color itself in its neighborhood.
+    \end{itemize}
+  \end{frame}
+
+  \begin{frame}
+    \frametitle{Conflict-Free Coloring}
+
+    \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+      \centering
+      \includegraphics[width=6.5cm]{../figures/example-cfcp.pdf}
+    \end{textblock*}
+
+    \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+      \centering
+      \includegraphics[width=6.5cm]{../figures/example-vcp.pdf}
+    \end{textblock*}
+
+    \vspace{3cm}
+
+    \begin{center}
+      Every vertex $v$ has at least one unique color within its neighborhood.
+    \end{center}
+
+    \begin{columns}
+
+      \pause
+
+      \begin{column}{0.5\textwidth}
+        \begin{itemize}[leftmargin=1.4cm]
+          \item[$v$ = 1:] $\{1: none,\ 2: none,\ 5: \textbf{red}\}$
+          \item[$v$ = 2:] $\{1: none,\ 2: none,\ 3: \textbf{blue},$ \newline $\quad 5: red,\ 6: none\}$
+          \item[$v$ = 3:] $\{2: none,\ 3: \textbf{blue}\}$
+        \end{itemize}
+      \end{column}
+
+      \pause
+
+      \begin{column}{0.5\textwidth}
+        \begin{itemize}[leftmargin=1.4cm]
+          \item[$v$ = 1:] $\{1: \textbf{blue},\ 2: red,\ 5: yellow\}$
+          \item[$v$ = 2:] $\{1: blue,\ 2: \textbf{red},\ 3: blue,$ \newline $\quad 5: yellow,\ 6: blue\}$
+          \item[$v$ = 3:] $\{2: red,\ 3: \textbf{blue}\}$
+        \end{itemize}
+      \end{column}
+
+    \end{columns}
+
+  \end{frame}
+
+  \begin{frame}
+    \frametitle{Conflict-Free Coloring Examples}
+
+    \begin{textblock*}{\examplewidth}(1cm,\exampleheight) % {block width} (coords)
+      Incorrect conflict-free colorings and their fixes:
+    \end{textblock*}
+
+    \vspace{0.5cm}
+
+    \pause
+
+    \begin{columns}
+      \begin{column}{0.33333\textwidth}
+        \only<2,4-7>{
           \begin{figure}[h]
             \centering
-      \includegraphics[width=8cm]{../figures/example-cfcp.pdf}
+            \includegraphics[width=3cm]{../figures/examples-1-incorrect-1.pdf}
           \end{figure}
+        }
 
-    \begin{itemize}
-      \item A \textbf{conflict-free coloring} of a graph $G$ assigns colors to some vertices such that there is a uniquely colored vertex within the closed neighborhood of every vertex.
-      \item Every proper vertex coloring of $G$ is also a conflict-free coloring of $G$. This is because every vertex can be its own conflict-free neighbor.
-    \end{itemize}
+        \only<3>{
+          \begin{figure}[h]
+            \centering
+            \includegraphics[width=3cm]{../figures/examples-1-incorrect-1-corrected.pdf}
+          \end{figure}
+        }
+
+        \centering
+        Vertex 1 does not have a unique color in its neighborhood.
+      \end{column}
+
+      \pause
+      \pause
+
+      \begin{column}{0.33333\textwidth}
+
+        \only<4,6-7>{
+        \begin{figure}[h]
+          \centering
+          \includegraphics[width=3cm]{../figures/examples-1-incorrect-2.pdf}
+        \end{figure}
+        }
+
+        \only<5>{
+        \begin{figure}[h]
+          \centering
+          \includegraphics[width=3cm]{../figures/examples-1-incorrect-2-corrected.pdf}
+        \end{figure}
+        }
+
+        \centering
+        Vertices $\{2, 3, 4\}$ do not have a unique color in their neighborhoods.
+      \end{column}
+
+      \pause
+      \pause
+
+      \begin{column}{0.33333\textwidth}
+
+        \only<6>{
+        \begin{figure}[h]
+          \centering
+          \includegraphics[width=3cm]{../figures/examples-1-incorrect-3.pdf}
+        \end{figure}
+        }
+
+        \only<7>{
+        \begin{figure}[h]
+          \centering
+          \includegraphics[width=3cm]{../figures/examples-1-incorrect-3-corrected.pdf}
+        \end{figure}
+        }
+
+        \centering
+        Vertex 3 does not have a unique color in its neighborhood.
+      \end{column}
+    \end{columns}
+
+    % \begin{textblock*}{\examplewidth}(0cm,1.3cm) % {block width} (coords)
+    %   \centering
+    %   \textbf{Incorrect} colorings
+    % \end{textblock*}
+    %
+    % \begin{textblock*}{\examplewidth}(0cm,2cm) % {block width} (coords)
+    %   \centering
+    %   \includegraphics[width=10cm]{../figures/examples-1-incorrect.pdf}
+    % \end{textblock*}
+    %
+    % \begin{textblock*}{\examplewidth}(0cm,5.2cm) % {block width} (coords)
+    %   \centering
+    %   Correct colorings
+    % \end{textblock*}
+    %
+    % \begin{textblock*}{\examplewidth}(0cm,6cm) % {block width} (coords)
+    %   \centering
+    %   \includegraphics[width=10cm]{../figures/examples-1-correct.pdf}
+    % \end{textblock*}
+
   \end{frame}

### 2017-04-10 presentation/presentation.tex
Making some minor fixes to presentation
Background and some applications done for presentation

@@
 \usepackage{xcolor}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 \usepackage[absolute,overlay]{textpos}
@@
 % {eso-pic}
+
+\setitemize{label=\usebeamerfont*{itemize item}%
+  \usebeamercolor[fg]{itemize item}
+  \usebeamertemplate{itemize item}}
 
@@
 \setbeamercolor{background canvas}{bg=white}
+\setbeamertemplate{caption}{\raggedright\insertcaption\par}
 
@@
       \centering
-      \includegraphics[width=14cm]{../figures/map-no-colors-1.pdf}
+      \includegraphics[width=14cm]{../figures/map-no-colors-3.pdf}
     \end{figure}
@@
 
-    \begin{columns}
-
     \pause
 
+    \begin{columns}
       \begin{column}{0.5\textwidth}
@@
       \end{column}
-
     \end{columns}
@@
       \begin{column}{0.33333\textwidth}
-        \only<2,4-7>{
+        \only<2>{
           \begin{figure}[h]
@@
 
-        \only<3>{
+        \only<3-7>{
           \begin{figure}[h]
@@
 
-        \only<4,6-7>{
+        \only<4>{
         \begin{figure}[h]
@@
 
-        \only<5>{
+        \only<5-7>{
         \begin{figure}[h]
@@
 
-    % \begin{textblock*}{\examplewidth}(0cm,1.3cm) % {block width} (coords)
-    %   \centering
-    %   \textbf{Incorrect} colorings
-    % \end{textblock*}
-    %
-    % \begin{textblock*}{\examplewidth}(0cm,2cm) % {block width} (coords)
-    %   \centering
-    %   \includegraphics[width=10cm]{../figures/examples-1-incorrect.pdf}
-    % \end{textblock*}
-    %
-    % \begin{textblock*}{\examplewidth}(0cm,5.2cm) % {block width} (coords)
-    %   \centering
-    %   Correct colorings
-    % \end{textblock*}
-    %
-    % \begin{textblock*}{\examplewidth}(0cm,6cm) % {block width} (coords)
-    %   \centering
-    %   \includegraphics[width=10cm]{../figures/examples-1-correct.pdf}
-    % \end{textblock*}
-
   \end{frame}
@@
 
+  \begin{frame}
+    \frametitle{Wireless Networks}
+
+    \begin{itemize}
+      \item \textbf{Wireless networks} such as cellular networks, television broadcasts, and satellite communication systems can all benefit from conflict-free coloring.
+
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=12cm]{../figures/towers-slides.pdf}
+      \end{figure}
+
+      \pause
+
+      \item A \textbf{cellular network} is a heterogeneous network with two types of nodes.
+
+      \pause
+
+      \begin{itemize}
+        \item Base-stations act as servers and are interconnected by an external backbone network.
+        \pause
+        \item Clients connect to base-stations via radio links. They constantly search for base-stations with strong reception.
+      \end{itemize}
+    \end{itemize}
+
+  \end{frame}
+
+  \begin{frame}
+    \frametitle{Cellular Networks}
+
+    \begin{itemize}
+      \item The problem when designing cellular networks: \textbf{frequency assignment}.
+      \begin{itemize}
+        \item Imagine two nearby base-stations having the same frequency.
+        \item A client in range of both base-stations would receive mutual interference.
+      \end{itemize}
+    \end{itemize}
+
+    \pause
+    \vspace{-0.2cm}
+
+    \begin{itemize}
+      \item This leads us to our goal: Assign frequencies such that:
+      \pause
+      \begin{itemize}
+        \item[(1)] Every client is served by a base-station with a unique frequency
+        \pause
+        \item[(2)] Minimize the number of frequencies used
+      \end{itemize}
+    \end{itemize}
+
+    \pause
+    \vfill
+
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
+      \caption{Vertex coloring and conflict-free coloring of cellular towers, respectively}
+    \end{figure}
+
+  \end{frame}
+
   \subsection{RFID Networks}
+
+  \begin{frame}
+    \frametitle{RFID Networks}
+  \end{frame}
 
@@
   \section{CF Coloring for General Graphs}
+  \subsection{Guaranteeing CF k-Colorability}
+  \begin{frame}
+    \frametitle{Guaranteeing CF k-Colorability}
+
+    It is wasteful to spend time coloring a graph that cannot be conflict-free colored within a certain amount of colors ($k$).
+Thus researchers came up with a criterion to guarantee a graph can be colored with $k$ colors.
+
+    \pause
+    \vfill
+
+    A \textbf{complete graph} is a graph where every pair of distinct vertices is connected by an edge.
+
+    \pause
+
+    \begin{itemize}
+      \item $K_n$: A complete graph of $n$ vertices.
+      \pause
+      \item $K_n^{-3}$: A complete graph of $n$ vertices with any three edges forming a triangle removed.
+    \end{itemize}
+
+    \pause
+    \vfill
+
+    \begin{theorem}
+    Let $G$ be a graph and $k \geq 1$. If $G$ has neither $K_{k+2}$ nor $K_{k+3}^{-3}$ as a minor, $G$ has a conflict-free coloring that can be found in polynomial time.
+    \end{theorem}
+
+  \end{frame}
+
+  \begin{frame}
+    \frametitle{Guaranteeing CF k-Colorability}
+
+  \end{frame}
+
+  \begin{frame}
+    \frametitle{Iterated Elimination of Distance-3-Sets}
+
+    \begin{algorithm}[H]
+    \caption{Test}
+    \scriptsize
+    \begin{algorithmic}[1]
+    \State $i \gets 1$
+    \State Remove all isolated paths from $G$
+    \While{$G$ is not empty}
+    	\State $D \gets \emptyset$
+    	\ForAll{components of $G$}
+    		\State Pick any vertex $v$
+    		\State $D \gets D \cup \{ v \}$
+    		\While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+    			\State Pick $u$ at distance 3 from some vertex in $D$
+    			\State $D \gets D \cup \{ w \}$
+    		\EndWhile
+    		\ForAll{$u \in D$}
+    			\State Color $u$ with color $i$
+    		\EndFor
+    		\State $i \gets i + 1$
+    		\ForAll{$u \in D$}
+    			\State Remove $N(u)$ from $G$
+    		\EndFor
+    		\State Remove all isolated paths from G
+    	\EndFor
+    \EndWhile
+    \State Color all removed isolated paths using color $i$
+    \end{algorithmic}
+  \end{algorithm}
+  \end{frame}
 

### 2017-04-10 presentation/presentation.tex
Adding guaranteeing CF coloring slides

@@
   \begin{frame}
-    \frametitle{Guaranteeing CF k-Colorability}
+    \frametitle{Guaranteeing Conflict-Free k-Colorability}
 
@@
   \begin{frame}
-    \frametitle{Guaranteeing CF k-Colorability}
+    \frametitle{Guaranteeing Conflict-Free k-Colorability}
+
+    % \begin{textblock*}{\examplewidth}(1cm,1.4cm) % {block width} (coords)
+    % \end{textblock*}
+
+    \begin{textblock*}{14cm}(1cm, 1.6cm) % {block width} (coords)
+      Let's demonstrate meeting this criterion on a graph for the simplest case, $k=1$:
+    \end{textblock*}
+
+    \begin{textblock*}{15cm}(0.5cm, 2.1cm) % {block width} (coords)
+      \only<1>{
+        \begin{figure}
+         \centering
+         \includegraphics[width=6cm]{../figures/criterion.pdf}
+         \caption{A simple, undirected graph $G$}
+       \end{figure}
+      }
+
+      \only<2>{
+        \vspace{0.25cm}
+        \begin{columns}
+          \begin{column}{0.5\textwidth}
+            \begin{center}
+              \begin{figure}
+                 \centering
+                 \includegraphics[width=6cm]{../figures/criterion.pdf}
+                 \caption{A simple, undirected graph $G$}
+               \end{figure}
+            \end{center}
+          \end{column}
+          \begin{column}{0.5\textwidth}
+            \begin{center}
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
+                \caption{Graphs $K_{3}$ and $K_{4}^{-3}$}
+              \end{figure}
+            \end{center}
+          \end{column}
+        \end{columns}
+      }
+
+      \only<3>{
+        \vspace{0.25cm}
+        \begin{columns}
+          \begin{column}{0.5\textwidth}
+            \begin{center}
+              \begin{figure}
+                 \centering
+                 \includegraphics[width=6cm]{../figures/criterion-minor.pdf}
+                 \caption{A simple, undirected graph $G$}
+               \end{figure}
+            \end{center}
+          \end{column}
+          \begin{column}{0.5\textwidth}
+            \begin{center}
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
+                \caption{Graphs $K_{3}$ and $K_{4}^{-3}$}
+              \end{figure}
+            \end{center}
+          \end{column}
+        \end{columns}
+      }
+    \end{textblock*}
+
+    \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
+      To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor.
+A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
+    \end{textblock*}
 

### 2017-04-10 presentation/presentation.tex
Working on algorithm presentation

@@
 \usepackage{xcolor}
-\usepackage{algorithm}
+\usepackage{algorithm, caption}
 \usepackage[noend]{algpseudocode}
 \usepackage[absolute,overlay]{textpos}
+\usepackage{calc}
 % \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
@@
 \newcommand{\examplewidth}{16cm}
+
+\makeatletter
+\newcommand{\algcolor}[2]{%
+  \hskip-\ALG@thistlm\colorbox{#1}{\raisebox{0pt}[0.1cm][0cm]{\parbox{\dimexpr\linewidth-2\fboxsep}{\hskip\ALG@thistlm\relax #2}}}%
+}
+\newcommand{\algemph}[1]{\algcolor{Yellow}{#1}}
+\makeatother
 
@@
 A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
+\only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
     \end{textblock*}
@@
 
+    \only<1>{
+      \begin{columns}
+        \begin{column}{0.5\textwidth}
           \begin{algorithm}[H]
-    \caption{Test}
+            \caption*{\textbf{Algorithm} IEDS}
             \scriptsize
@@
           \end{algorithm}
+        \end{column}
+        \begin{column}{0.5\textwidth}
+          \begin{center}
+            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
+                \caption*{A simple, undirected graph $G$}
+              \end{figure}
+            \end{textblock*}
+          \end{center}
+        \end{column}
+      \end{columns}
+    }
+
+    \only<2-6>{
+      \begin{textblock*}{8cm}(8cm, 6cm) % {block width} (coords)
+        \begin{center}
+          $i= 1$
+        \end{center}
+      \end{textblock*}
+    }
+
+    \only<2>{
+      \begin{columns}
+        \begin{column}{0.5\textwidth}
+          \begin{algorithm}[H]
+            \caption*{\textbf{Algorithm} IEDS}
+            \scriptsize
+            \begin{algorithmic}[1]
+            \State \algemph{$i \gets 1$}
+            \State \algemph{Remove all isolated paths from $G$}
+            \While{$G$ is not empty}
+              \State $D \gets \emptyset$
+              \ForAll{components of $G$}
+                \State Pick any vertex $v$
+                \State $D \gets D \cup \{ v \}$
+                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+                  \State Pick $u$ at distance 3 from some vertex in $D$
+                  \State $D \gets D \cup \{ w \}$
+                \EndWhile
+                \ForAll{$u \in D$}
+                  \State Color $u$ with color $i$
+                \EndFor
+                \State $i \gets i + 1$
+                \ForAll{$u \in D$}
+                  \State Remove $N(u)$ from $G$
+                \EndFor
+                \State Remove all isolated paths from G
+              \EndFor
+            \EndWhile
+            \State Color all removed isolated paths using color $i$
+            \end{algorithmic}
+          \end{algorithm}
+        \end{column}
+        \begin{column}{0.5\textwidth}
+          \begin{center}
+            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
+                \caption*{A simple, undirected graph $G$}
+              \end{figure}
+            \end{textblock*}
+          \end{center}
+        \end{column}
+      \end{columns}
+    }
+
+    \only<3>{
+      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
+        \begin{center}
+          $D= \{\}$
+        \end{center}
+      \end{textblock*}
+
+      \begin{columns}
+        \begin{column}{0.5\textwidth}
+          \begin{algorithm}[H]
+            \caption*{\textbf{Algorithm} IEDS}
+            \scriptsize
+            \begin{algorithmic}[1]
+            \State $i \gets 1$
+            \State Remove all isolated paths from $G$
+            \While{$G$ is not empty}
+              \State \algemph{$D \gets \emptyset$}
+              \ForAll{components of $G$}
+                \State Pick any vertex $v$
+                \State $D \gets D \cup \{ v \}$
+                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+                  \State Pick $u$ at distance 3 from some vertex in $D$
+                  \State $D \gets D \cup \{ w \}$
+                \EndWhile
+                \ForAll{$u \in D$}
+                  \State Color $u$ with color $i$
+                \EndFor
+                \State $i \gets i + 1$
+                \ForAll{$u \in D$}
+                  \State Remove $N(u)$ from $G$
+                \EndFor
+                \State Remove all isolated paths from G
+              \EndFor
+            \EndWhile
+            \State Color all removed isolated paths using color $i$
+            \end{algorithmic}
+          \end{algorithm}
+        \end{column}
+        \begin{column}{0.5\textwidth}
+          \begin{center}
+            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
+                \caption*{A simple, undirected graph $G$}
+              \end{figure}
+            \end{textblock*}
+          \end{center}
+        \end{column}
+      \end{columns}
+    }
+
+    \only<4>{
+      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
+        \begin{center}
+          $D= \{8\}$
+        \end{center}
+      \end{textblock*}
+
+      \begin{columns}
+        \begin{column}{0.5\textwidth}
+          \begin{algorithm}[H]
+            \caption*{\textbf{Algorithm} IEDS}
+            \scriptsize
+            \begin{algorithmic}[1]
+            \State $i \gets 1$
+            \State Remove all isolated paths from $G$
+            \While{$G$ is not empty}
+              \State $D \gets \emptyset$
+              \ForAll{components of $G$}
+                \State \algemph{Pick any vertex $v$}
+                \State \algemph{$D \gets D \cup \{ v \}$}
+                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+                  \State Pick $u$ at distance 3 from some vertex in $D$
+                  \State $D \gets D \cup \{ w \}$
+                \EndWhile
+                \ForAll{$u \in D$}
+                  \State Color $u$ with color $i$
+                \EndFor
+                \State $i \gets i + 1$
+                \ForAll{$u \in D$}
+                  \State Remove $N(u)$ from $G$
+                \EndFor
+                \State Remove all isolated paths from G
+              \EndFor
+            \EndWhile
+            \State Color all removed isolated paths using color $i$
+            \end{algorithmic}
+          \end{algorithm}
+        \end{column}
+        \begin{column}{0.5\textwidth}
+          \begin{center}
+            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
+                \caption*{A simple, undirected graph $G$}
+              \end{figure}
+            \end{textblock*}
+          \end{center}
+        \end{column}
+      \end{columns}
+    }
+
+    \only<5>{
+      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
+        \begin{center}
+          $D= \{8\}$
+        \end{center}
+      \end{textblock*}
+
+      \begin{columns}
+        \begin{column}{0.5\textwidth}
+          \begin{algorithm}[H]
+            \caption*{\textbf{Algorithm} IEDS}
+            \scriptsize
+            \begin{algorithmic}[1]
+            \State $i \gets 1$
+            \State Remove all isolated paths from $G$
+            \While{$G$ is not empty}
+              \State $D \gets \emptyset$
+              \ForAll{components of $G$}
+                \State Pick any vertex $v$}
+                \State $D \gets D \cup \{ v \}$
+                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+                  \State Pick $u$ at distance 3 from some vertex in $D$
+                  \State $D \gets D \cup \{ w \}$
+                \EndWhile
+                \ForAll{$u \in D$}
+                  \State Color $u$ with color $i$
+                \EndFor
+                \State $i \gets i + 1$
+                \ForAll{$u \in D$}
+                  \State Remove $N(u)$ from $G$
+                \EndFor
+                \State Remove all isolated paths from G
+              \EndFor
+            \EndWhile
+            \State Color all removed isolated paths using color $i$
+            \end{algorithmic}
+          \end{algorithm}
+        \end{column}
+        \begin{column}{0.5\textwidth}
+          \begin{center}
+            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
+              \begin{figure}
+                \centering
+                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
+                \caption*{A simple, undirected graph $G$}
+              \end{figure}
+            \end{textblock*}
+          \end{center}
+        \end{column}
+      \end{columns}
+    }
+
   \end{frame}

### 2017-04-10 presentation/presentation.tex
Adding line highlighting for algorithm presentation

@@
 
+% \makeatletter
+% \newcommand{\algcolor}[2]{%
+%   \hskip-\ALG@thistlm\colorbox{#1}{\raisebox{0pt}[0.1cm][0cm]{\parbox{\dimexpr\linewidth-2\fboxsep}{\hskip\ALG@thistlm\relax #2}}}%
+% }
+% \newcommand{\algemph}[1]{\algcolor{Yellow}{#1}}
+% \makeatother
+
+\usepackage{tikz}
+\usetikzlibrary{calc}
+
 \makeatletter
-\newcommand{\algcolor}[2]{%
-  \hskip-\ALG@thistlm\colorbox{#1}{\raisebox{0pt}[0.1cm][0cm]{\parbox{\dimexpr\linewidth-2\fboxsep}{\hskip\ALG@thistlm\relax #2}}}%
+% code borrowed from Andrew Stacey; See
+% http://tex.stackexchange.com/a/50054/3954
+\tikzset{%
+  remember picture with id/.style={%
+    remember picture,
+    overlay,
+    save picture id=#1,
+  },
+  save picture id/.code={%
+    \edef\pgf@temp{#1}%
+    \immediate\write\pgfutil@auxout{%
+      \noexpand\savepointas{\pgf@temp}{\pgfpictureid}}%
+  },
+  if picture id/.code args={#1#2#3}{%
+    \@ifundefined{save@pt@#1}{%
+      \pgfkeysalso{#3}%
+    }{
+      \pgfkeysalso{#2}%
     }
-\newcommand{\algemph}[1]{\algcolor{Yellow}{#1}}
+  }
+}
+
+\def\savepointas#1#2{%
+  \expandafter\gdef\csname save@pt@#1\endcsname{#2}%
+}
+
+\def\tmk@labeldef#1,#2\@nil{%
+  \def\tmk@label{#1}%
+  \def\tmk@def{#2}%
+}
+
+\tikzdeclarecoordinatesystem{pic}{%
+  \pgfutil@in@,{#1}%
+  \ifpgfutil@in@%
+    \tmk@labeldef#1\@nil
+  \else
+    \tmk@labeldef#1,(0pt,0pt)\@nil
+  \fi
+  \@ifundefined{save@pt@\tmk@label}{%
+    \tikz@scan@one@point\pgfutil@firstofone\tmk@def
+  }{%
+  \pgfsys@getposition{\csname save@pt@\tmk@label\endcsname}\save@orig@pic%
+  \pgfsys@getposition{\pgfpictureid}\save@this@pic%
+  \pgf@process{\pgfpointorigin\save@this@pic}%
+  \pgf@xa=\pgf@x
+  \pgf@ya=\pgf@y
+  \pgf@process{\pgfpointorigin\save@orig@pic}%
+  \advance\pgf@x by -\pgf@xa
+  \advance\pgf@y by -\pgf@ya
+  }%
+}
+
 \makeatother
+% end of Andrew's code
+
+% main command to draw the colored background
+\newcounter{mymark}
+\newcommand\ColorLine{%
+  \stepcounter{mymark}%
+  \tikz[remember picture with id=mark-\themymark,overlay] {;}%
+  \begin{tikzpicture}[remember picture,overlay]%
+    \filldraw[Yellow]%
+   let \p1=(pic cs:mark-\themymark),
+   \p2=(current page.east)  in
+   ([xshift=-0.3em,yshift=-0.7ex]0,\y1)  rectangle ++([xshift=-8.26cm]\x2,\baselineskip);
+  \end{tikzpicture}%
+}%
+
+% colored loops and declarations
+\makeatletter
+\algnewcommand\CREQUIRE{\item[\ColorLine\algorithmicrequire]}%
+\algnewcommand\CENSURE{\item[\ColorLine\algorithmicensure]}%
+\algnewcommand\CSTATE{\State\ColorLine}%
+\algnewcommand\CSTATEx{\Statex\ColorLine}%
+\algnewcommand\CCOMMENT{\Comment\ColorLine}%
+
+% \algdef{SE}[WHILE]{CWhile}{EndWhile}%
+%    [2][default]{\ColorLine\algorithmicwhile\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
+%    {\algorithmicend\ \algorithmicwhile}%
+ \algdef{SE}[WHILE]{CWhile}{EndWhile}[1]{\ColorLine\algorithmicwhile\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicwhile}%
+
+\algdef{SE}[FOR]{CFOR}{ENDFOR}%
+   [2][default]{\ColorLine\algorithmicfor\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
+   {\algorithmicend\ \algorithmicfor}%
+\algdef{S}[FOR]{CFORALL}%
+   [2][default]{\ColorLine\algorithmicforall\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
+\algdef{SE}[LOOP]{CLOOP}{ENDLOOP}%
+   [1][default]{\ColorLine\algorithmicloop\ALG@compatcomm{#1}}%
+   {\algorithmicend\ \algorithmicloop}%
+\algdef{SE}[REPEAT]{CREPEAT}{UNTIL}%
+   [1][default]{\ColorLine\algorithmicrepeat\ALG@compatcomm{#1}}%
+   [1]{\algorithmicuntil\ #1}%
+\algdef{SE}[IF]{CIF}{ENDIF}%
+   [2][default]{\ColorLine\algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
+   {\algorithmicend\ \algorithmicif}%
+\algdef{C}[IF]{IF}{CELSIF}%
+   [2][default]{\ColorLine\algorithmicelse\ \algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
+\algdef{Ce}[ELSE]{IF}{CELSE}{ENDIF}%
+   [1][default]{\ColorLine\algorithmicelse\ALG@compatcomm{#1}}%
+\makeatother
+\algtext*{EndWhile}%
 
@@
             \begin{algorithmic}[1]
-            \State \algemph{$i \gets 1$}
-            \State \algemph{Remove all isolated paths from $G$}
+            \CSTATE $i \gets 1$
+            \CSTATE Remove all isolated paths from $G$
             \While{$G$ is not empty}
@@
             \While{$G$ is not empty}
-              \State \algemph{$D \gets \emptyset$}
+              \CSTATE $D \gets \emptyset$
               \ForAll{components of $G$}
@@
               \ForAll{components of $G$}
-                \State \algemph{Pick any vertex $v$}
-                \State \algemph{$D \gets D \cup \{ v \}$}
+                \CSTATE Pick any vertex $v$
+                \CSTATE $D \gets D \cup \{ v \}$
                 \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
@@
               \ForAll{components of $G$}
-                \State Pick any vertex $v$}
+                \State Pick any vertex $v$
                 \State $D \gets D \cup \{ v \}$
-                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
+                \CWhile{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                   \State Pick $u$ at distance 3 from some vertex in $D$

### 2017-04-10 presentation/presentation.tex
Finishing IEDS algorithm example for presentation

@@
 
-\algdef{SE}[FOR]{CFOR}{ENDFOR}%
-   [2][default]{\ColorLine\algorithmicfor\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
-   {\algorithmicend\ \algorithmicfor}%
-\algdef{S}[FOR]{CFORALL}%
-   [2][default]{\ColorLine\algorithmicforall\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
+% \algdef{SE}[FOR]{CFOR}{ENDFOR}%
+%    [2][default]{\ColorLine\algorithmicfor\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
+%    {\algorithmicend\ \algorithmicfor}%
+% \algdef{S}[FOR]{CFORALL}%
+%    [2][default]{\ColorLine\algorithmicforall\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
+
+\algdef{SE}[FOR]{For}{EndFor}[1]{\algorithmicfor\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicfor}%
+
+\algdef{S}[FOR]{CForAll}[1]{\ColorLine\algorithmicforall\ #1\ \algorithmicdo}%
+
 \algdef{SE}[LOOP]{CLOOP}{ENDLOOP}%
@@
 \algtext*{EndWhile}%
+\algtext*{EndFor}%
 
@@
 
-    \only<1>{
-      \begin{columns}
-        \begin{column}{0.5\textwidth}
-          \begin{algorithm}[H]
-            \caption*{\textbf{Algorithm} IEDS}
-            \scriptsize
-            \begin{algorithmic}[1]
-            \State $i \gets 1$
-            \State Remove all isolated paths from $G$
-            \While{$G$ is not empty}
-              \State $D \gets \emptyset$
-              \ForAll{components of $G$}
-                \State Pick any vertex $v$
-                \State $D \gets D \cup \{ v \}$
-                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
-                  \State Pick $u$ at distance 3 from some vertex in $D$
-                  \State $D \gets D \cup \{ w \}$
-                \EndWhile
-                \ForAll{$u \in D$}
-                  \State Color $u$ with color $i$
-                \EndFor
-                \State $i \gets i + 1$
-                \ForAll{$u \in D$}
-                  \State Remove $N(u)$ from $G$
-                \EndFor
-                \State Remove all isolated paths from G
-              \EndFor
-            \EndWhile
-            \State Color all removed isolated paths using color $i$
-            \end{algorithmic}
-          \end{algorithm}
-        \end{column}
-        \begin{column}{0.5\textwidth}
-          \begin{center}
-            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
-              \begin{figure}
-                \centering
-                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
-                \caption*{A simple, undirected graph $G$}
-              \end{figure}
-            \end{textblock*}
-          \end{center}
-        \end{column}
-      \end{columns}
-    }
-
-    \only<2-6>{
-      \begin{textblock*}{8cm}(8cm, 6cm) % {block width} (coords)
-        \begin{center}
-          $i= 1$
-        \end{center}
-      \end{textblock*}
-    }
-
-    \only<2>{
-      \begin{columns}
-        \begin{column}{0.5\textwidth}
-          \begin{algorithm}[H]
-            \caption*{\textbf{Algorithm} IEDS}
-            \scriptsize
-            \begin{algorithmic}[1]
-            \CSTATE $i \gets 1$
-            \CSTATE Remove all isolated paths from $G$
-            \While{$G$ is not empty}
-              \State $D \gets \emptyset$
-              \ForAll{components of $G$}
-                \State Pick any vertex $v$
-                \State $D \gets D \cup \{ v \}$
-                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
-                  \State Pick $u$ at distance 3 from some vertex in $D$
-                  \State $D \gets D \cup \{ w \}$
-                \EndWhile
-                \ForAll{$u \in D$}
-                  \State Color $u$ with color $i$
-                \EndFor
-                \State $i \gets i + 1$
-                \ForAll{$u \in D$}
-                  \State Remove $N(u)$ from $G$
-                \EndFor
-                \State Remove all isolated paths from G
-              \EndFor
-            \EndWhile
-            \State Color all removed isolated paths using color $i$
-            \end{algorithmic}
-          \end{algorithm}
-        \end{column}
-        \begin{column}{0.5\textwidth}
-          \begin{center}
-            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
-              \begin{figure}
-                \centering
-                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
-                \caption*{A simple, undirected graph $G$}
-              \end{figure}
-            \end{textblock*}
-          \end{center}
-        \end{column}
-      \end{columns}
-    }
-
-    \only<3>{
-      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
-        \begin{center}
-          $D= \{\}$
-        \end{center}
-      \end{textblock*}
-
-      \begin{columns}
-        \begin{column}{0.5\textwidth}
-          \begin{algorithm}[H]
-            \caption*{\textbf{Algorithm} IEDS}
-            \scriptsize
-            \begin{algorithmic}[1]
-            \State $i \gets 1$
-            \State Remove all isolated paths from $G$
-            \While{$G$ is not empty}
-              \CSTATE $D \gets \emptyset$
-              \ForAll{components of $G$}
-                \State Pick any vertex $v$
-                \State $D \gets D \cup \{ v \}$
-                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
-                  \State Pick $u$ at distance 3 from some vertex in $D$
-                  \State $D \gets D \cup \{ w \}$
-                \EndWhile
-                \ForAll{$u \in D$}
-                  \State Color $u$ with color $i$
-                \EndFor
-                \State $i \gets i + 1$
-                \ForAll{$u \in D$}
-                  \State Remove $N(u)$ from $G$
-                \EndFor
-                \State Remove all isolated paths from G
-              \EndFor
-            \EndWhile
-            \State Color all removed isolated paths using color $i$
-            \end{algorithmic}
-          \end{algorithm}
-        \end{column}
-        \begin{column}{0.5\textwidth}
-          \begin{center}
-            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
-              \begin{figure}
-                \centering
-                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
-                \caption*{A simple, undirected graph $G$}
-              \end{figure}
-            \end{textblock*}
-          \end{center}
-        \end{column}
-      \end{columns}
-    }
-
-    \only<4>{
-      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
-        \begin{center}
-          $D= \{8\}$
-        \end{center}
-      \end{textblock*}
-
-      \begin{columns}
-        \begin{column}{0.5\textwidth}
-          \begin{algorithm}[H]
-            \caption*{\textbf{Algorithm} IEDS}
-            \scriptsize
-            \begin{algorithmic}[1]
-            \State $i \gets 1$
-            \State Remove all isolated paths from $G$
-            \While{$G$ is not empty}
-              \State $D \gets \emptyset$
-              \ForAll{components of $G$}
-                \CSTATE Pick any vertex $v$
-                \CSTATE $D \gets D \cup \{ v \}$
-                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
-                  \State Pick $u$ at distance 3 from some vertex in $D$
-                  \State $D \gets D \cup \{ w \}$
-                \EndWhile
-                \ForAll{$u \in D$}
-                  \State Color $u$ with color $i$
-                \EndFor
-                \State $i \gets i + 1$
-                \ForAll{$u \in D$}
-                  \State Remove $N(u)$ from $G$
-                \EndFor
-                \State Remove all isolated paths from G
-              \EndFor
-            \EndWhile
-            \State Color all removed isolated paths using color $i$
-            \end{algorithmic}
-          \end{algorithm}
-        \end{column}
-        \begin{column}{0.5\textwidth}
-          \begin{center}
-            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
-              \begin{figure}
-                \centering
-                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
-                \caption*{A simple, undirected graph $G$}
-              \end{figure}
-            \end{textblock*}
-          \end{center}
-        \end{column}
-      \end{columns}
-    }
-
-    \only<5>{
-      \begin{textblock*}{8cm}(8cm, 6.5cm) % {block width} (coords)
-        \begin{center}
-          $D= \{8\}$
-        \end{center}
-      \end{textblock*}
-
-      \begin{columns}
-        \begin{column}{0.5\textwidth}
-          \begin{algorithm}[H]
-            \caption*{\textbf{Algorithm} IEDS}
-            \scriptsize
-            \begin{algorithmic}[1]
-            \State $i \gets 1$
-            \State Remove all isolated paths from $G$
-            \While{$G$ is not empty}
-              \State $D \gets \emptyset$
-              \ForAll{components of $G$}
-                \State Pick any vertex $v$
-                \State $D \gets D \cup \{ v \}$
-                \CWhile{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
-                  \State Pick $u$ at distance 3 from some vertex in $D$
-                  \State $D \gets D \cup \{ w \}$
-                \EndWhile
-                \ForAll{$u \in D$}
-                  \State Color $u$ with color $i$
-                \EndFor
-                \State $i \gets i + 1$
-                \ForAll{$u \in D$}
-                  \State Remove $N(u)$ from $G$
-                \EndFor
-                \State Remove all isolated paths from G
-              \EndFor
-            \EndWhile
-            \State Color all removed isolated paths using color $i$
-            \end{algorithmic}
-          \end{algorithm}
-        \end{column}
-        \begin{column}{0.5\textwidth}
-          \begin{center}
-            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
-              \begin{figure}
-                \centering
-                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
-                \caption*{A simple, undirected graph $G$}
-              \end{figure}
-            \end{textblock*}
-          \end{center}
-        \end{column}
-      \end{columns}
-    }
+    \input{ieds}
 

### 2017-04-10 presentation/presentation.tex
CF by dominating set algorithm presentation

@@
 \usepackage{calc}
+\usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
+
 % \usepackage[texcoord,grid,gridunit=mm,gridcolor=red!10,subgridcolor=green!10]
@@
 
+  \subsection{Iterated Elimination of Distance-3-Sets}
+
   \begin{frame}
@@
   \section{CF Coloring for Planar Graphs}
+
+  \subsection{Bounds for Planar Graphs}
+  \begin{frame}
+    \frametitle{Bounds on Planar Graphs}
+
+    \only<3>{
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/four.pdf}
+        \caption*{A vertex and conflict-free coloring, respectively}
+      \end{figure}
+    }
+
+    \begin{theorem}
+    Every loopless planar graph admits a proper \textbf{vertex coloring} with at most {\color{red} four} distinct colors.
+    \end{theorem}
+
+    \pause
+
+    \begin{theorem}
+    Every loopless planar graph admits a \textbf{conflict-free coloring} with at most {\color{red} three} distinct colors.
+    \end{theorem}
+
+  \end{frame}
+
+  \subsection{Dominating Set Algorithm}
+  \begin{frame}
+    \frametitle{Conflict-Free Coloring via Dominating Set}
+
+    \input{dominating}
+  \end{frame}
 

### 2017-04-10 presentation/presentation.tex
Adding future work to presentation

@@
 
+  \begin{frame}
+    \frametitle{Future Work}
+
+    \begin{itemize}
+      \item Finding bounds and properties on specific graphs such as outerplanar graphs, interval graphs, hypergraphs, and more.
+      \pause
+      \vfill
+      \begin{itemize}
+        \item Allows for accurate estimates when applying conflict-free coloring to real-world problems.
+      \end{itemize}
+      \pause
+      \vfill
+      \item Variations of conflict-free coloring such as requiring \textbf{another} vertex to have a unique color within the neighborhood of a selected vertex.
+      \pause
+      \vfill
+      \begin{itemize}
+        \item Guiding a robot (unique color 1) to a destination (unique color 2).
+      \end{itemize}
+    \end{itemize}
+
+  \end{frame}
+
   \begin{frame}[standout]

### 2017-04-10 presentation/presentation.tex
Ready for first practice talk

@@
 
+  \addtocontents{toc}{\protect\vspace{-14pt}}
+
   \section{Background}
@@
 
-    \only<1-2>{
+    \only<1-3,6,9,11>{
       \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
@@
 
-    \only<3> {
+    \only<4> {
       \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
@@
 
-    \only<4> {
+    \only<5> {
       \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
@@
 
-    \vspace{4cm}
+    \only<7> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-dist-1.pdf}
+      \end{textblock*}
+    }
+
+    \only<8,10> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-dist-2.pdf}
+      \end{textblock*}
+    }
+
+    \only<12> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-dom-1.pdf}
+      \end{textblock*}
+    }
+
+    \only<13> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-dom-2.pdf}
+      \end{textblock*}
+    }
+
+    \vspace{3.5cm}
 
@@
 
+    \only<1-2>{
       \begin{itemize}
-      \item<1-4> A \textbf{graph} is the set of vertices \emph{V} and a set of edges \emph{E}.
-      \item<2-4> The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$ plus $v$ itself.
-      \only<1-2>{\item<3> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
-      \only<3>{\item<3> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
-      \only<4>{\item<4> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
+        \item<1-2> A \textbf{graph} is a set of vertices \emph{V} and a set of edges \emph{E}.
+        \pause
+        \item A \textbf{planar graph} is a graph that can be drawn on a plane such that no edges overlap.
       \end{itemize}
+    }
+
+    \only<3-5>{
+      \begin{itemize}
+        \item<3-5> The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$ plus $v$ itself.
+        \only<3>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
+        \only<4>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
+        \only<5>{\item<5> Example: The neighborhood of vertex 5: $\{1, 2, 4, 5, 6\}$.}
+      \end{itemize}
+    }
+
+    \only<6-8>{
+      \begin{itemize}
+        \item The \textbf{distance} is the smallest number of edges needed to cross to get from vertex $v$ to vertex $u$.
+        \only<6>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
+        \only<7>{\item<7> Example: Distance from vertex 1 to 6: \textbf{2}.}
+        \only<8>{\item<8> Example: Distance from vertex 3 to 4: \textbf{3}.}
+      \end{itemize}
+    }
+
+    \only<9-10>{
+      \begin{itemize}
+        \item A \textbf{distance-3-set} is a set containing all vertices that have exactly distance 3 from each other.
+        \only<9>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
+        \only<10>{\item<10> Example: The only possible distance-3-set: $\{3, 4\}$.}
+      \end{itemize}
+    }
+
+    \only<11-13>{
+      \begin{itemize}
+        \item A \textbf{dominating set} is a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
+        \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
+        \only<12>{\item<12> Example: $\{2, 5\}$}
+        \only<13>{\item<13> Example: $\{2, 4\}$}
+      \end{itemize}
+    }
 
@@
 
-  \subsection{Graph Coloring}
+  \subsection{Vertex Coloring}
 
@@
       \item A proper \textbf{vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
+      \pause
       \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
@@
   \end{frame}
+
+  \subsection{Conflict-Free Coloring}
 
@@
 
-  \addtocontents{toc}{\protect\vspace{14pt}}
+  % \addtocontents{toc}{\protect\vspace{14pt}}
 
-  \section{Applications}
+  \subsection{Applications}
 
-  \subsection{Wireless Networks}
+  \addtocontents{toc}{\protect\vspace{21pt}}
 
@@
       \begin{itemize}
-        \item[(1)] Every client is served by a base-station with a unique frequency
+        \item[(1)] Every client is served by a base-station with a unique frequency.
         \pause
-        \item[(2)] Minimize the number of frequencies used
+        \item[(2)] Minimize the number of frequencies used.
       \end{itemize}
@@
       \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
-      \caption{Vertex coloring and conflict-free coloring of cellular towers, respectively}
+      \caption*{Vertex coloring and conflict-free coloring of cellular towers, respectively}
     \end{figure}
@@
 
-  \subsection{RFID Networks}
+  % \subsection{RFID Networks}
+  %
+  % \begin{frame}
+  %   \frametitle{RFID Networks}
+  % \end{frame}
 
-  \begin{frame}
-    \frametitle{RFID Networks}
-  \end{frame}
+  %
 
@@
   \section{CF Coloring for General Graphs}
-  \subsection{Guaranteeing CF k-Colorability}
+  \subsection{Guaranteeing k-Colorability}
   \begin{frame}
@@
          \includegraphics[width=6cm]{../figures/criterion.pdf}
-         \caption{A simple, undirected graph $G$}
+         \caption*{A simple, undirected graph $G$}
        \end{figure}
@@
                  \includegraphics[width=6cm]{../figures/criterion.pdf}
-                 \caption{A simple, undirected graph $G$}
+                 \caption*{A simple, undirected graph $G$}
                \end{figure}
@@
                 \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
-                \caption{Graphs $K_{3}$ and $K_{4}^{-3}$}
+                \caption*{Graphs $K_{3}$ and $K_{4}^{-3}$}
               \end{figure}
@@
                  \includegraphics[width=6cm]{../figures/criterion-minor.pdf}
-                 \caption{A simple, undirected graph $G$}
+                 \caption*{A simple, undirected graph $G$}
                \end{figure}
@@
 
-  \subsection{Iterated Elimination of Distance-3-Sets}
+  \subsection{Distance-3-Sets Algorithm}
 
@@
 
-  \section{CF Coloring for Planar Graphs}
+  \addtocontents{toc}{\protect\vspace{7pt}}
+
+  \section{Coloring for Planar Graphs}
 

### 2017-04-13 presentation/presentation.tex
Making some fixes to the presentation

@@
 \usepackage[backend=bibtex,citestyle=authortitle]{biblatex}
+\usepackage[no-math]{fontspec}
 
@@
 
+\setsansfont[ItalicFont={Fira Sans Light Italic},%
+             BoldFont={Fira Sans Bold},%
+             BoldItalicFont={Fira Sans Italic}]%
+            {Fira Sans Light}
+
 \title{Conflict-Free Vertex Coloring of Planar Graphs}
@@
       \centering
-      \includegraphics[width=14cm]{../figures/map-no-colors-3.pdf}
+      \includegraphics[width=14cm]{../figures/map-no-colors-1.pdf}
     \end{figure}
@@
       \begin{itemize}
-        \item<1-2> A \textbf{graph} is a set of vertices \emph{V} and a set of edges \emph{E}.
+        \item<1-2> \textbf{Simple graph}: undirected graph with no loops.
         \pause
-        \item A \textbf{planar graph} is a graph that can be drawn on a plane such that no edges overlap.
+        \vfill
+        \item \textbf{Planar graph}: no edges overlap.
       \end{itemize}
@@
       \begin{itemize}
-        \item<3-5> The \textbf{neighborhood} of a vertex $v$ is a set of all vertices adjacent to $v$ plus $v$ itself.
+        \item<3-5> \textbf{Neighborhood} of a vertex $v$: a set of all vertices adjacent to $v$ plus $v$.
+        \vfill
         \only<3>{\item<4> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
@@
       \begin{itemize}
-        \item The \textbf{distance} is the smallest number of edges needed to cross to get from vertex $v$ to vertex $u$.
-        \only<6>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
-        \only<7>{\item<7> Example: Distance from vertex 1 to 6: \textbf{2}.}
-        \only<8>{\item<8> Example: Distance from vertex 3 to 4: \textbf{3}.}
+        \item \textbf{Distance}: smallest number of edges to get from one vertex to another.
+        \vfill
+        \only<6>{\item<7> Example: distance from vertex 1 to 3: \textbf{2}.}
+        \only<7>{\item<7> Example: distance from vertex 1 to 6: \textbf{2}.}
+        \only<8>{\item<8> Example: distance from vertex 3 to 4: \textbf{3}.}
       \end{itemize}
@@
       \begin{itemize}
-        \item A \textbf{distance-3-set} is a set containing all vertices that have exactly distance 3 from each other.
+        \item \textbf{Distance-3-set}: contains all vertices with exactly distance 3 from each other.
+        \vfill
         \only<9>{\item<7> Example: Distance from vertex 1 to 3: \textbf{2}.}
@@
     \only<11-13>{
+    \vspace{0.55cm}
       \begin{itemize}
-        \item A \textbf{dominating set} is a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
+        \item \textbf{Dominating set}: a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
+        \vfill
         \only<11>{\item<7> Example: The neighborhood of vertex 1: $\{1, 2, 5\}$.}
@@
 
-    \vspace{4cm}
+    \vspace{4.5cm}
     \vfill
@@
     \begin{itemize}
-      \item A proper \textbf{vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
+      \item A \textbf{proper vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
       \pause
+      \vfill
       \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
@@
     \begin{itemize}
-      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that there is a uniquely colored vertex within the neighborhood of every vertex.
-      \item<2> Every proper vertex coloring of $G$ is also a conflict-free coloring of $G$ as every vertex $v$ would be a unique color itself in its neighborhood.
+      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that the neighborhood of every vertex contains at least one unique color.
+      \vfill
+      \pause
+      \item<2> Proper vertex colorings are also conflict-free colorings.
     \end{itemize}
@@
 
-  \section{CF Coloring for General Graphs}
+  \section{Coloring for General Graphs}
   \subsection{Guaranteeing k-Colorability}

### 2017-04-14 presentation/presentation.tex
Working on more slides

@@
       \begin{column}{0.33333\textwidth}
-        \only<2>{
-          \begin{figure}[h]
+        \centering
+        \vspace{4.5cm}
+        Isolated vertex
+        \only<2-7>{
+          \begin{textblock*}{\examplewidth/3}(0.15cm,3.5cm) % {block width} (coords)
             \centering
             \includegraphics[width=3cm]{../figures/examples-1-incorrect-1.pdf}
-          \end{figure}
+          \end{textblock*}
         }
@@
         \only<3-7>{
-          \begin{figure}[h]
+          \begin{textblock*}{\examplewidth/3}(0.15cm,6.7cm) % {block width} (coords)
             \centering
             \includegraphics[width=3cm]{../figures/examples-1-incorrect-1-corrected.pdf}
-          \end{figure}
+          \end{textblock*}
         }
 
-        \centering
-        Vertex 1 does not have a unique color in its neighborhood.
       \end{column}
@@
       \begin{column}{0.33333\textwidth}
+        \centering
+        \vspace{4.5cm}
+        Triangle
 
-        \only<4>{
-        \begin{figure}[h]
+        \only<4-7>{
+          \begin{textblock*}{\examplewidth/3}(\examplewidth/3,3.5cm) % {block width} (coords)
             \centering
             \includegraphics[width=3cm]{../figures/examples-1-incorrect-2.pdf}
-        \end{figure}
+          \end{textblock*}
         }
@@
         \only<5-7>{
-        \begin{figure}[h]
+          \begin{textblock*}{\examplewidth/3}(\examplewidth/3,6.7cm) % {block width} (coords)
             \centering
             \includegraphics[width=3cm]{../figures/examples-1-incorrect-2-corrected.pdf}
-        \end{figure}
+          \end{textblock*}
         }
 
-        \centering
-        Vertices $\{2, 3, 4\}$ do not have a unique color in their neighborhoods.
       \end{column}
@@
       \begin{column}{0.33333\textwidth}
+        \centering
+        \vspace{4.5cm}
+        Missing unique
 
-        \only<6>{
-        \begin{figure}[h]
+        \only<6-7>{
+          \begin{textblock*}{\examplewidth/3}(10.57cm,3.5cm) % {block width} (coords)
             \centering
             \includegraphics[width=3cm]{../figures/examples-1-incorrect-3.pdf}
-        \end{figure}
+          \end{textblock*}
         }
@@
         \only<7>{
-        \begin{figure}[h]
+          \begin{textblock*}{\examplewidth/3}(10.57cm,6.7cm) % {block width} (coords)
             \centering
             \includegraphics[width=3cm]{../figures/examples-1-incorrect-3-corrected.pdf}
-        \end{figure}
+          \end{textblock*}
         }
-
-        \centering
-        Vertex 3 does not have a unique color in its neighborhood.
       \end{column}
@@
   \begin{frame}
-    \frametitle{Wireless Networks}
+    \frametitle{Applications}
 
     \begin{itemize}
-      \item \textbf{Wireless networks} such as cellular networks, television broadcasts, and satellite communication systems can all benefit from conflict-free coloring.
+      \item \textbf{Applications}: wireless networks, satellite communication systems, RFID networks.
+
+      \pause
+      \vfill
 
@@
 
+      \vfill
+
+      \item \textbf{Cellular networks}: consist of base-stations and clients.
       \pause
+      \item The problem: \textbf{frequency assignment}.
 
-      \item A \textbf{cellular network} is a heterogeneous network with two types of nodes.
+    \end{itemize}
 
+  \end{frame}
+
+  \begin{frame}
+    \frametitle{Cellular Networks}
+
+    \only<1>{
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers-slides-2.pdf}
+      \end{figure}
+    }
+
+    \only<2->{
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers-slides-3.pdf}
+      \end{figure}
+    }
+
+    \pause
     \pause
@@
     \begin{itemize}
-        \item Base-stations act as servers and are interconnected by an external backbone network.
+      \item Our goal is to assign frequencies such that:
       \pause
-        \item Clients connect to base-stations via radio links. They constantly search for base-stations with strong reception.
+      \begin{itemize}
+        \item[(1)] Every client is served by a base-station with a unique frequency.
+        \pause
+        \item[(2)] Minimize the number of frequencies used.
       \end{itemize}
@@
 
-    \begin{itemize}
-      \item The problem when designing cellular networks: \textbf{frequency assignment}.
-      \begin{itemize}
-        \item Imagine two nearby base-stations having the same frequency.
-        \item A client in range of both base-stations would receive mutual interference.
-      \end{itemize}
-    \end{itemize}
-
-    \pause
-    \vspace{-0.2cm}
-
-    \begin{itemize}
-      \item This leads us to our goal: Assign frequencies such that:
-      \pause
-      \begin{itemize}
-        \item[(1)] Every client is served by a base-station with a unique frequency.
-        \pause
-        \item[(2)] Minimize the number of frequencies used.
-      \end{itemize}
-    \end{itemize}
-
-    \pause
-    \vfill
+    \begin{figure}[h]
+      \centering
+      \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers-graph.pdf}
+    \end{figure}
 
@@
       \centering
-      \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
+      \includegraphics[width=10cm,trim=4 4 4 4,clip]{../figures/towers.pdf}
       \caption*{Vertex coloring and conflict-free coloring of cellular towers, respectively}
@@
 
-    It is wasteful to spend time coloring a graph that cannot be conflict-free colored within a certain amount of colors ($k$).
-Thus researchers came up with a criterion to guarantee a graph can be colored with $k$ colors.
-
-    \pause
-    \vfill
-
-    A \textbf{complete graph} is a graph where every pair of distinct vertices is connected by an edge.
+    We want to guarantee a graph can be colored with $k$ colors.
 
@@
 
+    \only<1-2>{
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-1.pdf}
+        \caption*{Graphs $K_3$ and $K_4$, respectively}
+      \end{figure}
+    }
+
+    \only<3>{
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-2.pdf}
+        \caption*{Graphs $K_3$ and $K_4$, respectively}
+      \end{figure}
+    }
+
+    \only<4>{
+      \begin{figure}[h]
+        \centering
+        \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion.pdf}
+        \caption*{Graphs $K_3$ and $K_4$, respectively}
+      \end{figure}
+    }
+
+    \vfill
+
     \begin{itemize}
-      \item $K_n$: A complete graph of $n$ vertices.
+      \item \textbf{Complete graph}: every pair of distinct vertices is connected by an edge.
+      \vfill
       \pause
-      \item $K_n^{-3}$: A complete graph of $n$ vertices with any three edges forming a triangle removed.
+      \item \textbf{Tattered graph}: complete graph with a triangle removed.
     \end{itemize}
 
-    \pause
-    \vfill
+  \end{frame}
 
-    \begin{theorem}
-    Let $G$ be a graph and $k \geq 1$. If $G$ has neither $K_{k+2}$ nor $K_{k+3}^{-3}$ as a minor, $G$ has a conflict-free coloring that can be found in polynomial time.
-    \end{theorem}
-
-  \end{frame}
+  % \begin{theorem}
+  % Let $G$ be a graph and $k \geq 1$. If $G$ has neither $K_{k+2}$ nor $K_{k+3}^{-3}$ as a minor, $G$ has a conflict-free coloring that can be found in polynomial time.
+  % \end{theorem}
 
@@
     \begin{textblock*}{14cm}(1cm, 7.1cm) % {block width} (coords)
+      A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
 To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor.
-A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
 \only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}

### 2017-04-15 presentation/presentation.tex
Pretty close to done with presentation

@@
       \begin{itemize}
-        \item<1-2> \textbf{Simple graph}: undirected graph with no loops.
+        \item \textbf{Simple graph}: undirected graph with no loops.
         \pause
         \vfill
-        \item \textbf{Planar graph}: no edges overlap.
+        \item \textbf{Planar graph}: no edges cross.
       \end{itemize}
@@
       \begin{itemize}
-        \item<3-5> \textbf{Neighborhood} of a vertex $v$: a set of all vertices adjacent to $v$ plus $v$.
+        \item<3-5> \textbf{Neighborhood} of a vertex: a set of all adjacent vertices and the vertex itself.
         \vfill
@@
       \begin{itemize}
-        \item \textbf{Dominating set}: a subset of vertices $D$ of $V$ such that every vertex \emph{not} in $D$ is adjacent to at least one vertex in $D$.
+        \item \textbf{Dominating set}: all vertices outside of the set must have distance 1 to some vertex within the set.
         \vfill
@@
     \begin{itemize}
-      \item A \textbf{proper vertex coloring} of a graph $G$ assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
+      \item A \textbf{proper vertex coloring} assigns colors to \emph{every} vertex such that no two adjacent vertices share the same color.
       \pause
       \vfill
-      \item The \textbf{chromatic number} of $G$ is the minimum number of colors needed to properly color $G$.
+      \item The \textbf{chromatic number} is the minimum number of colors needed to properly color a graph.
     \end{itemize}
@@
     \begin{itemize}
-      \item<1-2> A \textbf{conflict-free coloring} of a graph $G$ assigns colors to \emph{some} vertices such that the neighborhood of every vertex contains at least one unique color.
+      \item<1-2> A \textbf{conflict-free coloring} assigns colors to \emph{some} vertices such that the neighborhood of every vertex contains at least one uniquely colored vertex.
       \vfill
@@
 
-    \begin{center}
-      Every vertex $v$ has at least one unique color within its neighborhood.
-    \end{center}
-
     \pause
@@
       \begin{column}{0.5\textwidth}
+        \begin{multicols}{2}
           \begin{itemize}[leftmargin=1.4cm]
-          \item[$v$ = 1:] $\{1: none,\ 2: none,\ 5: \textbf{red}\}$
-          \item[$v$ = 2:] $\{1: none,\ 2: none,\ 3: \textbf{blue},$ \newline $\quad 5: red,\ 6: none\}$
-          \item[$v$ = 3:] $\{2: none,\ 3: \textbf{blue}\}$
+            \item[1:] \textbf{red}
+            \pause
+            \item[2:] \textbf{blue}
+            \pause
+            \item[3:] \textbf{blue}
+            \pause
+            \item[4:] \textbf{red}
+            \pause
+            \item[5:] \textbf{red}
+            \pause
+            \item[6:] \textbf{red}
           \end{itemize}
+        \end{multicols}
       \end{column}
@@
       \begin{column}{0.5\textwidth}
+        \begin{multicols}{2}
           \begin{itemize}[leftmargin=1.4cm]
-          \item[$v$ = 1:] $\{1: \textbf{blue},\ 2: red,\ 5: yellow\}$
-          \item[$v$ = 2:] $\{1: blue,\ 2: \textbf{red},\ 3: blue,$ \newline $\quad 5: yellow,\ 6: blue\}$
-          \item[$v$ = 3:] $\{2: red,\ 3: \textbf{blue}\}$
+            \item[1:] \textbf{blue}
+            \pause
+            \item[2:] \textbf{red}
+            \pause
+            \item[3:] \textbf{blue}
+            \pause
+            \item[4:] \textbf{red}
+            \pause
+            \item[5:] \textbf{yellow}
+            \pause
+            \item[6:] \textbf{blue}
           \end{itemize}
+        \end{multicols}
       \end{column}
@@
         \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-1.pdf}
-        \caption*{Graphs $K_3$ and $K_4$, respectively}
+        \caption*{Complete 3 vertex and complete 4 vertex graphs}
       \end{figure}
@@
         \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion-2.pdf}
-        \caption*{Graphs $K_3$ and $K_4$, respectively}
+        \caption*{Complete 3 vertex and complete 4 vertex graphs}
       \end{figure}
@@
         \includegraphics[width=8cm,trim=4 4 4 4,clip]{../figures/bad-criterion.pdf}
-        \caption*{Graphs $K_3$ and $K_4$, respectively}
+        \caption*{Complete 3 vertex and tattered 4 vertex graphs}
       \end{figure}
@@
     \begin{textblock*}{14cm}(1cm, 1.6cm) % {block width} (coords)
-      Let's demonstrate meeting this criterion on a graph for the simplest case, $k=1$:
+      Let's demonstrate meeting this criterion on a graph for the simplest case, 1 color.
     \end{textblock*}
@@
          \includegraphics[width=6cm]{../figures/criterion.pdf}
-         \caption*{A simple, undirected graph $G$}
+         \caption*{A simple graph}
        \end{figure}
@@
                  \includegraphics[width=6cm]{../figures/criterion.pdf}
-                 \caption*{A simple, undirected graph $G$}
+                 \caption*{A simple graph}
                \end{figure}
@@
                 \includegraphics[width=6cm]{../figures/bad-criterion.pdf}
-                \caption*{Graphs $K_{3}$ and $K_{4}^{-3}$}
+                \caption*{Complete 3 vertex and tattered 4 vertex graphs}
               \end{figure}
@@
                  \includegraphics[width=6cm]{../figures/criterion-minor.pdf}
-                 \caption*{A simple, undirected graph $G$}
+                 \caption*{A simple graph}
                \end{figure}
@@
       }
+
+      \only<4>{
+        \begin{textblock*}{14cm}(1cm, 3.5cm) % {block width} (coords)
+          \begin{theorem}
+          A graph cannot be conflict-free colored with $k$ colors if it contains a complete graph of $k+2$ vertices or a tattered graph of $k+3$ vertices.
+          \end{theorem}
+        \end{textblock*}
+      }
     \end{textblock*}
@@
       A graph is a \textbf{minor} if it can be formed by deleting and/or contracting edges from its parent graph.
-To be conflict-free colored with 1 color, graph $G$ cannot contain $K_3$ or $K_4^{-3}$ as a minor.
-\only<3>{$G$ contains both $K_3$ and $K_4^{-3}$ as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
+\only<3->{$G$ contains both graphs as a minor and thus {\color{red}\textbf{cannot}} be conflict-free colored with 1 color.}
     \end{textblock*}

### 2017-04-15 presentation/presentation.tex
Last minute changes

@@
 
-    \only<8,10> {
+    \only<8> {
       \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
@@
         \includegraphics[width=8cm]{../figures/example-dist-2.pdf}
+      \end{textblock*}
+    }
+
+    \only<10> {
+      \begin{textblock*}{\examplewidth}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=8cm]{../figures/example-d3s.pdf}
       \end{textblock*}
@@
       \begin{itemize}
-        \item \textbf{Dominating set}: all vertices outside of the set must have distance 1 to some vertex within the set.
+        \item \textbf{Dominating set}: all vertices not in the set must have distance 1 to some vertex within the set.
         \vfill
@@
 
+    \only<1, 8->{
       \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
@@
       \end{textblock*}
+    }
 
+    \only<2>{
+      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-cf-1.pdf}
+      \end{textblock*}
+    }
+
+    \only<3>{
+      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-cf-2.pdf}
+      \end{textblock*}
+    }
+
+    \only<4>{
+      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-cf-3.pdf}
+      \end{textblock*}
+    }
+
+    \only<5>{
+      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-cf-4.pdf}
+      \end{textblock*}
+    }
+
+    \only<6>{
+      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-cf-5.pdf}
+      \end{textblock*}
+    }
+
+    \only<7>{
+      \begin{textblock*}{\examplewidth/2}(0cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-cf-6.pdf}
+      \end{textblock*}
+    }
+
+    \only<1-7>{
       \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
@@
       \end{textblock*}
+    }
+
+    \only<8>{
+      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-vcp-1.pdf}
+      \end{textblock*}
+    }
+
+    \only<9>{
+      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-vcp-2.pdf}
+      \end{textblock*}
+    }
+
+    \only<10>{
+      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-vcp-3.pdf}
+      \end{textblock*}
+    }
+
+    \only<11>{
+      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-vcp-4.pdf}
+      \end{textblock*}
+    }
+
+    \only<12>{
+      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-vcp-5.pdf}
+      \end{textblock*}
+    }
+
+    \only<13>{
+      \begin{textblock*}{\examplewidth/2}(8cm,\exampleheight) % {block width} (coords)
+        \centering
+        \includegraphics[width=6.5cm]{../figures/example-vcp-6.pdf}
+      \end{textblock*}
+    }
 
@@
 
-      \item \textbf{Cellular networks}: consist of base-stations and clients.
+      \item \textbf{Cellular networks}: consist of towers and clients.
       \pause
@@
       \begin{itemize}
-        \item[(1)] Every client is served by a base-station with a unique frequency.
+        \item[(1)] Every client is served by a tower with a unique frequency.
         \pause
@@
           \begin{theorem}
-          A graph cannot be conflict-free colored with $k$ colors if it contains a complete graph of $k+2$ vertices or a tattered graph of $k+3$ vertices.
+          A graph cannot be conflict-free colored with $k$ colors if it contains a complete graph of $k+2$ vertices or a tattered graph of $k+3$ vertices as a minor.
           \end{theorem}

### 2017-04-16 paper/paper.tex
Making changes to paper based on external review

@@
 While some problems are relatively easy to solve, the vertex coloring problem is one of the most computationally complex problems in computer science and mathematics \cite{bondy1976graph}.
-The vertex coloring problem has many real-world applications such as exam timetabling, register allocation, and the scheduling of taxis.
+The vertex coloring problem has many real-world applications such as finding the minimum number of time slots needed to schedule final exam periods such that no two courses (taken by the same student) are scheduled at the same time slot.
 
 The \emph{conflict-free coloring} problem is a relaxed variation of the vertex coloring problem.
-The conflict-free coloring problem does not aim to color every vertex such that it is not connected to a vertex of the same color.
-Rather, it aims to color \emph{enough} vertices such that for every vertex, there is a unique color assigned to a vertex within its closed neighborhood.
+The conflict-free coloring problem does not aim to color \emph{every} vertex such that it is not connected to a vertex of the same color.
+Rather, it aims to color \emph{some} vertices such that the neighborhood of every vertex contains at least one unqiuely colored vertex.
 
@@
 For example, $\{u, w\} \in E$ is an edge connecting vertices $u$ and $w$ where $u,w \in V$.
-Vertices are adjacent if they are connected by an edge.
-A simple graph is an undirected graph where each edge connects two different vertices and no two edges connect the same pair of vertices.
+Vertices are \emph{adjacent} if they are connected by an edge.
+An edge that connects a vertex to itself is called a \emph{loop}.
+A graph without loops is called \emph{loopless}.
+
+A simple graph is a loopless graph where no two edges connect the same pair of vertices.
 A planar graph is a graph that can be drawn on the plane such that its edges only intersect at their endpoints.
 This drawing is referred to as a planar drawing.
-All graphs used by the vertex coloring problem and conflict-free coloring problem will be undirected, simple graphs.
-An example graph that we will use later on is shown in figure \ref{fig:graph}.
+All graphs used by the vertex coloring problem and conflict-free coloring problem are assumed to be simple graphs.
+An example simple graph that we will use later on is shown in Figure \ref{fig:graph}.
 
@@
 A \emph{closed} neighborhood consists the vertices adjacent to $v$ plus $v$ itself.
-Unless stated otherwise, we will assume when writing about neighborhoods that they are closed neighborhoods.
-For example, let's examine $N_{G_1}(1)$ from figure  \ref{fig:graph}.
+For example, let's examine $N_{G_1}(1)$ from Figure \ref{fig:graph}.
 The open neighborhood of 1 is $\{2, 5\}$ while the closed neighborhood is $\{1, 2, 5\}$.
+For the rest of the paper, the term \emph{neighborhood} will refer to closed neighborhoods unless stated otherwise.
 
 A \emph{path} is a sequence of edges that connect a sequence of distinct vertices.
-A component of a graph $G$ is a subgraph $H$ where $H$ is connected and $H$ is not contained in any connected subgraph of $G$ that has more vertices or edges than $H$ has.
+A \emph{subgraph} is a graph $H$ that can be formed from a subset of the vertices and edges of $G$.
+A graph is \emph{connected} if there exists a path between every pair of vertices.
+A \emph{component} of a graph $G$ is a subgraph $H$ where $H$ is connected and $H$ is not contained in any connected subgraph of $G$ that has more vertices or edges than $H$ has.
 An isolated path is a component that is itself a path.
 
-The distance of a path can be thought of the smallest number of edges needed to be crossed to get from one vertex to another vertex.
-For example, in figure \ref{fig:graph}, the distance from vertex 3 to vertex 4 would be 3 as it takes 3 edges to get there.
+The distance of a path can be thought of as the smallest number of edges needed to get from one vertex to another vertex.
+For example, in Figure \ref{fig:graph}, the distance from vertex 3 to vertex 4 would be 3 as it takes 3 edges to get there.
 A \emph{distance-3-set} is a set of vertices that all have exactly distance 3 from each other.
-An example of a distance-3-set from figure \ref{fig:graph} would be $\{3,4\}$.
+An example of a distance-3-set from Figure \ref{fig:graph} would be $\{3,4\}$.
 \cite{bondy1976graph,west2001introduction}
@@
 \label{sec:coloring}
-A vertex coloring is an assignment of colors to each vertex of a graph $G$ such that no adjacent vertices share the same color.
+A \emph{vertex coloring} is an assignment of colors to each vertex of a graph $G$.
+A \emph{proper vertex coloring} assigns colors such that no two adjacent vertices share the same color.
 Mathematically, it can be described as a function $f : V \rightarrow S = \{1, 2, \dots, k\}$ such that $\forall u,w \in V$, if $(u,w) \in E$, then $f(u) \neq f(w)$.
-A vertex coloring that satisfies this constraint is called a \emph{proper coloring}.
 The \emph{chromatic number} of $G$, denoted $\chi(G)$, is the minimum number of colors, i.e.
 $|S|$, needed to properly color $G$.
-The \emph{vertex coloring} problem (VCP), when given a simple graph $G$, is to find $\chi(G)$.
+The \emph{vertex coloring problem} (VCP), when given a simple graph $G$, is to find $\chi(G)$.
 \cite{bondy1976graph}
@@
 A graph having $\chi(G) = k$ is said to be a \emph{k-chromatic} graph.
-The \emph{k-colorability} problem (CFCP) asks if a graph can be colored using $k$ colors.
+The \emph{k-colorability} problem asks if a graph can be colored using $k$ colors.
 This problem is slightly easier than the VCP as it is decision problem rather than an optimization problem.
-An example of a 3-colorable graph and a vertex coloring is shown in figure \ref{fig:vcp-example}.
+An example of a 3-colorable graph and a vertex coloring is shown in Figure \ref{fig:vcp-example}.
 
@@
 
-A \emph{conflict-free k-coloring} of a simple graph $G$ assigns one of $k$ different colors to a subset $P \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the closed neighborhood of $v$.
-The set $V \setminus S$ contains any uncolored vertices.
+A \emph{conflict-free k-coloring} of a simple graph $G$ assigns colors, $\{1, 2, \ldots, k\}$, to a subset $P \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the neighborhood of $v$.
+The set $V \setminus P$ contains any uncolored vertices.
 Generally, a \emph{conflict-free coloring} of a graph assigns colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
@@
 The \emph{conflict-free chromatic number} of G, denoted $\chi_{CF}(G)$, is the smallest $k$ for which a conflict-free coloring exists.
+The \emph{conflict-free coloring problem} (CFCP) aims to find $\chi_{CF}(G)$.
 \cite{abel2017three}
 
-An example of a conflict-free coloring is shown in figure \ref{fig:cfcp-example}.
+An example of a conflict-free coloring is shown in Figure \ref{fig:cfcp-example}.
 All uncolored vertices are in gray.
-It is a valid conflict-free coloring because every vertex has a unique color within its closed neighborhood.
+It is a valid conflict-free coloring because every vertex has a unique color within its neighborhood.
 For example, $N(1) = \{1: uncolored,\ 2: uncolored,\ 5: red\}$.
-Thus, red is the unique color within the closed neighborhood of vertex 1.
-We observe from figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
+Thus, red is the unique color within the neighborhood of vertex 1.
+We observe from Figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
 It is worth noting that all proper vertex colorings are also conflict-free colorings.
@@
 \label{sec:complexitytheory}
-A \emph{decision} problem, as mentioned earlier, is a problem that can be answered with a `yes' or a `no' \cite{sipser2006introduction}.
+A \emph{decision} problem, as mentioned earlier, is a problem that can be answered with `yes' or `no' \cite{sipser2006introduction}.
 A problem can be solved in polynomial time if an algorithm with input size $n$ can run in at most $n^k$ steps where $k$ is a constant that does not depend on $n$.
@@
 Base stations are each assigned a fixed frequency.
-Clients, however, are constantly searching frequencies in search for base-stations with good reception.
+Clients, however, are constantly searching frequencies for base-stations with strong reception.
 
@@
 The VCP model would require 3 colors, one for each base station.
-If we assign one base-station a color (say blue) and the other 2 (say red), then we only utilize two colors and the client utilizes the blue base-station and has no mutual interference.
-This model is shown in figure \ref{fig:towers}.
+If we assign one base-station a color (say blue) and the other 2 a \emph{different} color (say red), then we only utilize two colors and the client utilizes the blue base-station and has no mutual interference.
+This model is shown in Figure \ref{fig:towers}.
 This is exactly what a conflict-free coloring does.
@@
 The graph $K_n^{-3}$ is the graph obtained by removing any three edges forming a single triangle, i.e.
-\(K_n^{-3} =  \left ( V(K_n), E(K_n) \setminus E(K_3) \right ) \).
-A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed by deleting edges and/or contracting edges (combining the vertices of an edge) from $G$.
-\cite{abel2017three,bondy1976graph}
+$K_3$.
+
+A graph $H$ is called a \emph{minor} of a graph $G$ if $H$ can be formed by deleting edges and/or contracting edges (combining the vertices of an edge) from $G$. \cite{abel2017three,bondy1976graph}
 
@@
 Abel et al.
-give a criterion that guarantees k-colorability which is stated in theorem \ref{thm:criterion}.
+give a criterion that guarantees k-colorability which is stated in Theorem \ref{thm:criterion}.
 In the proof of this theorem, found in \cite{abel2017three}, the authors prove that their heuristic will always generate a k-colorable graph when the specified criterion is met.
-To illustrate this heuristic, we will generate a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined in algorithm \ref{alg:elimination}.
+To illustrate this heuristic, we will use a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined in Algorithm \ref{alg:elimination}.
 
 \subsection{Setting Up Example CF Coloring}
-We will demonstrate meeting the criterion to utilize this algorithm using the graph $G_2$ in figure \ref{fig:criterion}.
+Before demonstrating Algorithm \ref{alg:elimination}, we will demonstrate how to check if a graph, say $G_2$ in Figure \ref{fig:criterion}, meets the given criterion.
 
@@
 For $k = 1$, this means our graph cannot contain $K_{3}$ or $K_{4}^{-3}$ as a minor.
-These graphs are shown in figure \ref{fig:bad-criterion}.
+These graphs are shown in Figure \ref{fig:bad-criterion}.
 
@@
 We can see that $G_2$ has both of these as minors.
-The transformation needed to see the minors is shown in figure \ref{fig:criterion-minor}.
+The transformation needed to see the minors is shown in Figure \ref{fig:criterion-minor}.
 By contracting the dotted edges, vertices 1 and 4 would combine as well as vertices 3 and 5.
@@
 \label{sec:iterated}
-The iterated elimination of distance-3-sets algorithm is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in theorem \ref{thm:criterion}.
-If the criterion is not met, the heuristic will not generate a valid conflict-free k-coloring.
+The iterated elimination of distance-3-sets algorithm, given in \cite{abel2017three}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}.
+If the criterion is not met, the heuristic will not generate a valid conflict-free coloring of $k$ colors.
 
@@
 
-To illustrate this algorithm and show it produces a valid conflict-free coloring, we'll use graph $G_3$ shown in figure \ref{fig:algorithm1}.
+To illustrate this algorithm and show it produces a valid conflict-free coloring, we'll use graph $G_3$ shown in Figure \ref{fig:algorithm1}.
 The algorithm starts by setting a variable $i$, the current color, to a (color) 1.
@@
 Since $G_3$ is not empty, we enter the first $while$ loop and set a variable $D$ to the empty set.
-$G_3$ has only one component (the whole graph) so we will only iterate through the $for\ all$ on line 5 once.
+$G_3$ has only one component (the whole graph) so we will only iterate through the \emph{for all} on line 5 once.
 Pick any vertex from $G_3$, say vertex 8.
@@
 	\includegraphics[width=6cm]{../figures/algorithm1.pdf}
-	\caption{Graph $G_3$ to illustrate algorithm \ref{alg:elimination}}\label{fig:algorithm1}
+	\caption{Graph $G_3$ to illustrate Algorithm \ref{alg:elimination}}\label{fig:algorithm1}
 \end{figure}
@@
 We color all vertices in $D$, $\{2,8\}$, with color $i$ which is known as color 1 (say red).
-This coloring is shown in figure \ref{fig:algorithm1-step1}.
+This coloring is shown in Figure \ref{fig:algorithm1-step1}.
 We increase $i$ by one leading to $i \gets 2$.
@@
 By removing these vertices and any edges containing these vertices, we are left with vertices $\{5, 7\}$.
-This is shown in figure \ref{fig:algorithm1-step2}.
+This is shown in Figure \ref{fig:algorithm1-step2}.
 
@@
 This graph is not 1-colorable as it includes $K_3$ as a minor.
-As we have shown that this graph is 2-colorable and know it is not 1-colorable, we can conclude that $\chi_{CF}(G_3) = 2$.
+As we have shown that this graph is 2-colorable and Theorem \ref{thm:criterion} shows it is not 1-colorable, we can conclude that $\chi_{CF}(G_3) = 2$.
 
@@
 This is an example of a planar graph and illustrates a famous theorem associated with it.
-We present this theorem, called the four color theorem, in theorem \ref{thm:four}.
+We present this theorem, called the four color theorem, in Theorem \ref{thm:four}.
 The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.
@@
 
-Due to theorem \ref{thm:four}, we immediately know that every planar graph is conflict-free 4-colorable.
+Due to Theorem \ref{thm:four}, we immediately know that every planar graph is conflict-free 4-colorable.
 This raises the question of whether there are planar graphs that require four colors or if fewer colors could suffice for all planar graphs.
 This leads us to the conflict-free variation of this theorem.
-We present this in theorem \ref{thm:four-cf}.
+We present this in Theorem \ref{thm:four-cf}.
 It is given and proven in \cite{abel2017three}.
@@
 Figure \ref{fig:four} looks at a planar graph that requires four colors in a proper vertex coloring.
-Based on theorem \ref{thm:four-cf}, we know that this planar graph can be conflict-free colored with only three colors.
-This is shown in figure \ref{fig:four} as well.
+Based on Theorem \ref{thm:four-cf}, we know that this planar graph can be conflict-free colored with only three colors.
+This is shown in Figure \ref{fig:four} as well.
 
@@
 
-To demonstrate this algorithm, we will utilize graph $G_3$ as we did for algorithm \ref{alg:elimination}.
+To demonstrate this algorithm, we will utilize graph $G_3$ as we did for Algorithm \ref{alg:elimination}.
 It is a planar graph, so we can use this algorithm to generate a conflict-free coloring.
@@
 For small graphs, such as $G_3$, it is easy to find one by hand.
-A dominating set of $G_3, \{2, 6, 8\},$ is shown in figure \ref{fig:algorithm2-step1}.
+A dominating set of $G_3, \{2, 6, 8\},$ is shown in Figure \ref{fig:algorithm2-step1}.
 
@@
 We pick vertex $u$ to be vertex 2 because $2 \in D$ and $\{2, 3\} \in E$.
-We contract the edge and show the resulting graph $G$ in figure \ref{fig:algorithm2-step2}.
+We contract the edge and show the resulting graph $G$ in Figure \ref{fig:algorithm2-step2}.
 By iterating over the rest of the vertices in $V \setminus D$, we obtain a graph that is itself a path from vertex 2 to vertex 6 to vertex 8.
-This graph, along with its proper vertex coloring, is shown in figure \ref{fig:algorithm2-step3}.
+This graph, along with its proper vertex coloring, is shown in Figure \ref{fig:algorithm2-step3}.
 We can find a proper vertex coloring by any heuristic, such as a greedy algorithm, for the VCP.
@@
 We leave any nodes not in the graph $G$ uncolored when we color $G_3$.
-The coloring of $G_3$ is shown in figure \ref{fig:algorithm2-step4}.
+The coloring of $G_3$ is shown in Figure \ref{fig:algorithm2-step4}.
 It is clear that this has produced a conflict-free coloring.
@@
 
-Take note that this algorithm has produced fewer colored vertices than algorithm \ref{alg:elimination}.
+Take note that this algorithm has produced fewer colored vertices than Algorithm \ref{alg:elimination}.
 We had 4 colored vertices based on that algorithm where here we have 3.
@@
 
+\vspace{-0.3cm}
+
 \subsection{Minimizing Colored Vertices}
@@
 al \cite{abel2017three} present results on minimizing colored vertices when conflict-free coloring planar graphs.
-They propose and prove theorem \ref{thm:approximate-cfds} by using the polynomial-time algorithm described in algorithm \ref{alg:cf-dominating}.
+They propose and prove Theorem \ref{thm:approximate-cfds} by using the polynomial-time algorithm described in Algorithm \ref{alg:cf-dominating}.
 
@@
 
-We get a PTAS for the conflict-free domination number by applying algorithm \ref{alg:cf-dominating} and finding the dominating set using the PTAS defined by Baker and Hill \cite{baker1994approximation}.
+We get a PTAS for the conflict-free domination number by applying Algorithm \ref{alg:cf-dominating} and finding the dominating set using the PTAS defined by Baker and Hill \cite{baker1994approximation}.
 As the input graph $G$ is planar, the resulting graph $G'$ is also planar because $G'$ is a minor of $G$.
-Thus, it can be colored with 4 colors or less by \ref{thm:four}.
+Thus, it can be colored with 4 colors or less by Theorem \ref{thm:four}.
 We then color $G$ with the colors of $G'$, leaving any vertex in $G$ but not in $G'$ uncolored.
@@
 Although the CFCP is NP-hard and finding the minimum number colors needed requires inefficient brute force algorithms, there are heuristics to find good conflict-free colorings.
-It is still a recent problem in the world of computer science and mathematics, so research is still being conducted and proofs results are being presented.
 
@@
 \section{Acknowledgments}
-Thanks to Peter Dolan, Elena Machkasova, and Peh Ng for their advice and feedback.
+Thanks to Peter Dolan, Elena Machkasova, Peh Ng, and Jeremy Eberhardt for their advice and feedback.
 

### 2017-04-16 paper/paper.tex
Making minor format changes

@@
 
-The k-colorability problem and the conflict-free k-colorability problem are NP-complete.
+The k-colorability problem as well as the conflict-free k-colorability problem are NP-complete.
 This can be proven by using a reduction from a known NP-complete problem.
@@
 
-The problem when initially setting up these networks comes into play when assigning frequencies.
+The main problem when initially setting up these networks comes into play when assigning frequencies.
 Imagine two base-stations near each other having the same frequency.
@@
 
+\vspace{-0.5cm}
+
 \subsection{Iterated Elimination of Distance-3-Sets}
 \label{sec:iterated}
-The iterated elimination of distance-3-sets algorithm, given in \cite{abel2017three}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}.
+The iterated elimination of distance-3-sets algorithm, defined in \cite{abel2017three}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}.
 If the criterion is not met, the heuristic will not generate a valid conflict-free coloring of $k$ colors.

### 2017-05-01 paper/paper.tex
Last edits to paper before final copy

@@
 The conflict-free coloring problem aims to color a possibly proper subset of vertices such that there is a unique color within the closed neighborhood (a vertex and its neighbors) of every vertex.
-This paper presents recent heuristics to solve the conflict-free coloring problem on both general graphs and planar graphs.
+This paper presents recent findings and heuristics to solve the conflict-free coloring problem on both general graphs and planar graphs.
 \end{abstract}
@@
 All graphs used by the vertex coloring problem and conflict-free coloring problem are assumed to be simple graphs.
-An example simple graph that we will use later on is shown in Figure \ref{fig:graph}.
+An example graph is shown in Figure \ref{fig:graph}.
 
 The neighborhood of a vertex, denoted $N_G(v)$, is a set of all vertices adjacent to $v$.
-A \emph{closed} neighborhood consists the vertices adjacent to $v$ plus $v$ itself.
+A \emph{closed} neighborhood consists of the vertices adjacent to $v$ plus $v$ itself.
 For example, let's examine $N_{G_1}(1)$ from Figure \ref{fig:graph}.
@@
 The \emph{k-colorability} problem asks if a graph can be colored using $k$ colors.
-This problem is slightly easier than the VCP as it is decision problem rather than an optimization problem.
+This problem is slightly different than the VCP as it is decision problem rather than an optimization problem.
 An example of a 3-colorable graph and a vertex coloring is shown in Figure \ref{fig:vcp-example}.
@@
 For example, $N(1) = \{1: uncolored,\ 2: uncolored,\ 5: red\}$.
-Thus, red is the unique color within the neighborhood of vertex 1.
+As there are no other vertices colored red, we have verified there is a unique color in the neighborhood of vertex 1.
 We observe from Figures \ref{fig:vcp-example} and \ref{fig:cfcp-example}, $\chi(G_1) = 3$ and $\chi_{CF}(G_1) = 2$.
@@
 The k-colorability problem as well as the conflict-free k-colorability problem are NP-complete.
-This can be proven by using a reduction from a known NP-complete problem.
+This can be proven by using a reduction from a known NP-complete problem \cite{garey2002computers}.
 If we find a known hard problem $Y$, we can prove that another problem $X$ is hard by a reduction from $Y$ to $X$.
 The VCP and the CFCP have both been shown to be NP-hard \cite{abel2017three,moret1998theory}.
-The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, a well-known NP-complete problem \cite{sharma2012new}.
+The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, another well-known NP-complete problem \cite{sharma2012new}.
+The \emph{conflict-free k-colorability problem} is shown to be NP-complete by a reduction from k-colorability \cite{abel2017three}.
 
@@
 A complete graph on $n$ vertices is denoted as $K_n$.
-The graph $K_n^{-3}$ is the graph obtained by removing any three edges forming a single triangle, i.e.
+The graph $K_n^{-3}$ is the graph obtained by removing any three edges forming one single triangle, i.e.
 $K_3$.
@@
 give a criterion that guarantees k-colorability which is stated in Theorem \ref{thm:criterion}.
-In the proof of this theorem, found in \cite{abel2017three}, the authors prove that their heuristic will always generate a k-colorable graph when the specified criterion is met.
-To illustrate this heuristic, we will use a graph that fits the specified criterion and apply the iterated elimination of distance-3-sets algorithm defined in Algorithm \ref{alg:elimination}.
+In the proof of this theorem, found in \cite{abel2017three}, the authors prove that their heuristic, given in section \ref{sec:iterated}, will always generate a k-colorable graph when the specified criterion is met.
 
@@
 Graph $G_2$ is a simple graph with 6 vertices.
-It does not, however, fit our criterion; it actually breaks both properties as it has both $K_{k+2}$ and $K_{k+4}^{-3}$ as a minor.
 For $k = 1$, this means our graph cannot contain $K_{3}$ or $K_{4}^{-3}$ as a minor.
@@
 We would have both $K_{3}$ and $K_{4}^{-3}$.
+This graph does not fit our criterion; it even breaks both properties as it has both $K_{k+2}$ and $K_{k+4}^{-3}$ as a minor.
 Thus, this graph cannot be conflict-free colored with one color.
@@
 
-\vspace{-0.5cm}
+\vspace{-0.1cm}
 
@@
 \label{sec:iterated}
-The iterated elimination of distance-3-sets algorithm, defined in \cite{abel2017three}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}.
-If the criterion is not met, the heuristic will not generate a valid conflict-free coloring of $k$ colors.
+The iterated elimination of distance-3-sets algorithm, defined in \cite{abel2017three} and shown in Algorithm \ref{alg:elimination}, is a polynomial-time heuristic for generating a conflict-free k-coloring of general graphs that satisfy the criterion given in Theorem \ref{thm:criterion}.
+If the criterion is not met, the heuristic will produce a conflict-free coloring of more than $k$ colors.
 
@@
 The neighborhood of vertex 2 consists of $\{1,2,3,6\}$ and the neighborhood of vertex 8 consists of $\{4,8\}$.
-By removing these vertices and any edges containing these vertices, we are left with vertices $\{5, 7\}$.
-This is shown in Figure \ref{fig:algorithm1-step2}.
+By removing these vertices and any edges containing these vertices, we are left with vertices $\{5, 7\}$.~This is shown in Figure \ref{fig:algorithm1-step2}.
 
@@
 We present this theorem, called the four color theorem, in Theorem \ref{thm:four}.
-The proof by computer that is widely accepted today can be found in \cite{robertson1997four}.
+The most widely-accepted proof, which utilizes a computer to brute force every possible case, can be found in \cite{robertson1997four}.
 
@@
 Algorithm \ref{alg:elimination} presented in section \ref{sec:iterated} gives us an efficient heuristic for coloring general graphs including planar graphs.
-Algorithm \ref{alg:cf-dominating}, called conflict-free via dominating set, gives us another way of coloring planar graphs, albeit likely less efficient.
+Algorithm \ref{alg:cf-dominating}, called conflict-free via dominating set, gives us another way of coloring planar graphs, albeit likely less efficient with regards to running time.
 
@@
 
+\vspace{-0.1cm}
+
 \section{Conclusion}
 \label{sec:conclusion}
-I have presented some of the recent heuristics and findings on the conflict-free coloring problem.
+We have presented some of the recent heuristics and findings on the conflict-free coloring problem.
 Although the CFCP is NP-hard and finding the minimum number colors needed requires inefficient brute force algorithms, there are heuristics to find good conflict-free colorings.
@@
 the robot and its destination would both be a distinct unique color).
+Overall, finding properties and heuristics for conflict-free coloring is beneficial and required for efficiently solving real-world problems.
+
+\vspace{-0.1cm}
 

### 2017-05-01 paper/paper.tex
Camera ready... hopefully

@@
 The \emph{conflict-free coloring} problem is a relaxed variation of the vertex coloring problem.
-The conflict-free coloring problem does not aim to color \emph{every} vertex such that it is not connected to a vertex of the same color.
-Rather, it aims to color \emph{some} vertices such that the neighborhood of every vertex contains at least one unqiuely colored vertex.
+The conflict-free coloring problem does not aim to color \emph{every} vertex.
+Rather, it aims to color \emph{some} vertices such that the neighborhood of every vertex contains at least one uniquely colored vertex.
 
@@
 
-The neighborhood of a vertex, denoted $N_G(v)$, is a set of all vertices adjacent to $v$.
-A \emph{closed} neighborhood consists of the vertices adjacent to $v$ plus $v$ itself.
+The open neighborhood of a vertex is a set of all vertices adjacent to $v$.
+A \emph{closed} neighborhood, denoted $N_G(v)$, consists of the vertices adjacent to $v$ plus $v$ itself.
 For example, let's examine $N_{G_1}(1)$ from Figure \ref{fig:graph}.
@@
 For example, in Figure \ref{fig:graph}, the distance from vertex 3 to vertex 4 would be 3 as it takes 3 edges to get there.
-A \emph{distance-3-set} is a set of vertices that all have exactly distance 3 from each other.
+A \emph{distance-3-set} is a set of vertices that all have exactly pairwise distance 3 from each other.
 An example of a distance-3-set from Figure \ref{fig:graph} would be $\{3,4\}$.
@@
 Mathematically, it can be described as a function $f : V \rightarrow S = \{1, 2, \dots, k\}$ such that $\forall u,w \in V$, if $(u,w) \in E$, then $f(u) \neq f(w)$.
-The \emph{chromatic number} of $G$, denoted $\chi(G)$, is the minimum number of colors, i.e.
-$|S|$, needed to properly color $G$.
+The \emph{chromatic number} of $G$, denoted $\chi(G)$, is the minimum number of colors needed to properly color $G$.
 The \emph{vertex coloring problem} (VCP), when given a simple graph $G$, is to find $\chi(G)$.
@@
 The \emph{k-colorability} problem asks if a graph can be colored using $k$ colors.
-This problem is slightly different than the VCP as it is decision problem rather than an optimization problem.
+This problem is slightly different than the VCP as it is a decision problem rather than an optimization problem.
 An example of a 3-colorable graph and a vertex coloring is shown in Figure \ref{fig:vcp-example}.
@@
 A \emph{conflict-free k-coloring} of a simple graph $G$ assigns colors, $\{1, 2, \ldots, k\}$, to a subset $P \subseteq V$ of vertices such that $\forall v \in V$, there is a vertex $u \in N(v)$ where the color of $u$ is unique in the neighborhood of $v$.
-The set $V \setminus P$ contains any uncolored vertices.
+The set $V \setminus P$ is the uncolored vertices, if any.
 Generally, a \emph{conflict-free coloring} of a graph assigns colors to some of the vertices such that, for every vertex $v$, there is a unique color assigned to a vertex among $v$ and $v$'s neighbors.
@@
 A dominating set is a subset $D$ of $V$ such that every vertex not in $D$ is adjacent to at least one vertex in $D$.
+The set of colored vertices in a conflict-free coloring is a dominating set \cite{abel2017three}.
 The domination number of $G$, denoted $\gamma(G)$, is the size of a minimum dominating set of G.
+An example of a dominating set is $\{3, 5\}$ of graph $G_1$ where $\gamma(G_1) = 2$.
 The \emph{conflict-free domination number} for some $k$, denoted $\gamma_{CF}^k(G)$, is the minimum number of vertices that have to be colored in a conflict-free k-coloring of $G$.
-An example of a dominating set is $\{3, 5\}$ of graph $G_1$ where $\gamma(G_1) = 2$.
-The \emph{k-conflict-free dominating set} problem asks if a given k-coloring of a graph colors the minimum amount of vertices needed to have a coloring that utilizes $k$ colors.
+The \emph{k-conflict-free dominating set} problem asks if a given k-coloring of a graph colors the minimum amount of vertices needed to have a conflict-free coloring that utilizes $k$ colors.
 
@@
 The VCP and the CFCP have both been shown to be NP-hard \cite{abel2017three,moret1998theory}.
-The \emph{k-colorability} problem is proven to be NP-complete with a reduction from 3-SAT, another well-known NP-complete problem \cite{sharma2012new}.
-The \emph{conflict-free k-colorability problem} is shown to be NP-complete by a reduction from k-colorability \cite{abel2017three}.
+The k-colorability problem is proven to be NP-complete with a reduction from 3-SAT, another well-known NP-complete problem \cite{sharma2012new}.
+The conflict-free k-colorability problem is shown to be NP-complete by a reduction from k-colorability \cite{abel2017three}.
 
-It is often desirable and necessary to use approximation algorithms, known as heuristics, to solve complex problems like the VCP and the CFCP.
+It is often desirable and necessary to use approximation algorithms, called heuristics, to solve complex problems like the VCP and the CFCP.
 In our case, heuristics are polynomial-time algorithms that give good, but not optimal, solutions to our optimization problems.
 A polynomial-time approximation scheme (PTAS) is any polynomial-time approximation algorithm that takes an instance of an optimization problem and a parameter $\epsilon > 0$ and produces a solution that is within a factor $(1 + \epsilon)$ (for minimization problems) of being optimal.
+
+\vspace{-0.2cm}
 
@@
 
+\vspace{-0.1cm}
+
 This problem was initially modeled as a vertex coloring problem, where the vertices are the base-stations and the edges are the pairs of base-stations that overlap in their reception range.
@@
 We have a set of tags $P$ (i.e.
-automobile RFID chips).
+product RFID chips).
 We can say that $P$ is read by our schedule if for every tag $p \in P$, there is at least one reader $r \in R$ and a time $t$ such that $p$ is read by $r$ at time $t$.
@@
 The last step of the algorithm is to remove all isolated paths from $G$.
-Since we are left with only two vertices with no edges connecting them, we have 2 isolated paths.
+Since we are left with only two isolated vertices, which are trivially isolated paths, we have 2 isolated paths.
 We remove these isolated paths from $G$ and are left with an empty graph.
@@
 
-\vspace{-0.1cm}
+\vspace{-0.15cm}
 
@@
 It is easier to minimize frequency assignment for wireless networks and design RFID networks.
-Current research focuses on finding bounds and properties on specific cases such as planar graphs, interval graphs, types of hypergraphs, and more.
+Current research focuses on finding bounds and properties on specific cases such as interval graphs, types of hypergraphs, and more \cite{cheilaris2014strong,smorodinsky2013conflict}.
 
@@
 the robot and its destination would both be a distinct unique color).
-Overall, finding properties and heuristics for conflict-free coloring is beneficial and required for efficiently solving real-world problems.
+Relaxing the proper vertex coloring problem to satisfy new requirements leads to new heuristics that can effectively solve more real-world problems.
 
-\vspace{-0.1cm}
+\vspace{-0.15cm}
 
@@
 Thanks to Peter Dolan, Elena Machkasova, Peh Ng, and Jeremy Eberhardt for their advice and feedback.
+
+\vspace{-0.15cm}
 

### 2017-05-01 paper/paper.tex
Last minute changes

@@
 
-It is often desirable and necessary to use approximation algorithms, called heuristics, to solve complex problems like the VCP and the CFCP.
+It is often desirable and necessary to use approximation algorithms, known as heuristics, to solve complex problems like the VCP and the CFCP.
 In our case, heuristics are polynomial-time algorithms that give good, but not optimal, solutions to our optimization problems.
@@
 \begin{theorem} \label{thm:four}
-Every loopless planar graph admits a vertex coloring with at most four distinct colors.
+Every loopless planar graph admits a proper vertex coloring with at most four distinct colors.
 \end{theorem}
@@
 \begin{theorem} \label{thm:four-cf}
-Every loopless planar graph admits a conflict-free coloring with at most three distinct colors.
+Every loopless planar graph admits a valid conflict-free coloring with at most three distinct colors.
 \end{theorem}
